### 2024-03-07 paper/paper.qmd
update cleaned data, add tests, update variable name

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(here)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
# read in data
ces2020 <-  read_csv(here::here("data/analysis_data/cleaned_ces2020.csv"))
```

```{r}
# change column type to factor
ces2020 <-
  ces2020 |>
  mutate(
    voted_for = as_factor(voted_for),
    race = factor(
      race,
      levels = c(
        "White",
        "Black",
        "Hispanic",
        "Asian",
        "Native American",
        "Middle Eastern",
        "Two or more races",
        "Other"
      )
    ),
    region = factor(
      region,
      levels = c(
        "Northeast",
        "Midwest",
        "South",
        "West"
      )
    ),
    employ = factor(
      employ,
      levels = c(
        "Full-time",
        "Part-time",
        "Temporarily laid off",
        "Unemployed",
        "Retired",
        "Permanently disabled",
        "Homemaker",
        "Student",
        "Other"
      )
    )
  ) |>
  select(voted_for, race, region, employ)
```

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-03-07 scripts/01-download_data.R

@@ -14,7 +14,7 @@ library(tidyverse)
 
 
 #### Download data ####
-ces2020 <-
+raw_ces2020 <-
   get_dataframe_by_name(
     filename = "CES20_Common_OUTPUT_vv.csv",
     dataset = "10.7910/DVN/E9N6PH",
@@ -22,10 +22,10 @@ ces2020 <-
     .f = read_csv
   ) 
 
-ces2020 <-
-  ces2020 |>
+raw_ces2020 <-
+  raw_ces2020 |>
   select(votereg, CC20_410, race, region, employ)
 
 
 #### Save data ####
-write_csv(ces2020, "data/raw_data/ces2020.csv")
+write_csv(raw_ces2020, "data/raw_data/ces2020.csv")

### 2024-03-07 scripts/02-data_cleaning.R

@@ -28,10 +28,13 @@ raw_ces2020 <-
 # only interested in:
 # respondents who are registered to vote: votereg = 1
 # vote for Trump or Biden: CC20_410 = 1 Biden, 2 Trump
+# no NA in race, region
+# filter NA in employ
 cleaned_ces2020 <-
   raw_ces2020 |>
   filter(votereg == 1,
          CC20_410 %in% c(1, 2)) |>
+  filter(!is.na(employ)) |>
   mutate(
     voted_for = if_else(CC20_410 == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
@@ -45,33 +48,11 @@ cleaned_ces2020 <-
       race == 7 ~ "Two or more races",
       race == 8 ~ "Other"
     ),
-    race = factor(
-      race,
-      levels = c(
-        "White",
-        "Black",
-        "Hispanic",
-        "Asian",
-        "Native American",
-        "Middle Eastern",
-        "Two or more races",
-        "Other"
-      )
-    ),
     region = case_when(
       region == 1 ~ "Northeast",
       region == 2 ~ "Midwest",
       region == 3 ~ "South",
       region == 4 ~ "West"
-    ),
-    region = factor(
-      region,
-      levels = c(
-        "Northeast",
-        "Midwest",
-        "South",
-        "West"
-      )
     ),
     employ = case_when(
       employ == 1 ~ "Full-time",
@@ -83,21 +64,6 @@ cleaned_ces2020 <-
       employ == 7 ~ "Homemaker",
       employ == 8 ~ "Student",
       employ == 9 ~ "Other"
-      
-    ),
-    employ = factor(
-      employ,
-      levels = c(
-        "Full-time",
-        "Part-time",
-        "Temporarily laid off",
-        "Unemployed",
-        "Retired",
-        "Permanently disabled",
-        "Homemaker",
-        "Student",
-        "Other"
-      )
     )
   ) |>
   select(voted_for, race, region, employ)

### 2024-03-07 scripts/03-test_data.R

@@ -1,15 +1,100 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests the cleaned US CES 2020 data 
+# Author: Yimiao Yuan
+# Date: 06 March 2024
+# Contact: yymlinda.yuan@mail.utoronto.ca
+# License: --
+# Pre-requisites: run 01-download_data.R and 02-data_cleaning.R first to
+# get the cleaned dataset
+# Any other information needed? --
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
+# read in cleaned data
+cleaned_ces2020 <-  read_csv("data/analysis_data/cleaned_ces2020.csv")
+
+# check column class
+class(cleaned_ces2020$voted_for) == "character"
+class(cleaned_ces2020$race) == "character"
+class(cleaned_ces2020$region) == "character"
+class(cleaned_ces2020$employ) == "character"
+
+# range of data
+# voted_for
+correct_voted_for <- 
+  c("Trump", "Biden")
+
+if (all(cleaned_ces2020$voted_for |>
+        unique() %in% correct_voted_for)) 
+  {
+  "The cleaned voted_for match the expected voted_for"
+} else {
+  "Not all of the voted_for have been cleaned completely"
+}
+
+
+# race
+correct_race <-
+  c(
+    "White",
+    "Black",
+    "Hispanic",
+    "Asian",
+    "Native American",
+    "Middle Eastern",
+    "Two or more races",
+    "Other"
+  )
+
+if (all(cleaned_ces2020$race |>
+        unique() %in% correct_race)) 
+{
+  "The cleaned race match the expected race"
+} else {
+  "Not all of the race have been cleaned completely"
+}
+
+
+# region
+correct_region <-
+  c(
+    "Northeast",
+    "Midwest",
+    "South",
+    "West"
+  )
+
+if (all(cleaned_ces2020$region |>
+        unique() %in% correct_region)) 
+{
+  "The cleaned region match the expected region"
+} else {
[…]

### 2024-03-07 scripts/03-test_data.R
added readr library and new comments

@@ -11,20 +11,21 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(readr)
 
 
 #### Test data ####
 # read in cleaned data
 cleaned_ces2020 <-  read_csv("data/analysis_data/cleaned_ces2020.csv")
 
-# check column class
+# Check column class voted_for, race, region, and employ
 class(cleaned_ces2020$voted_for) == "character"
 class(cleaned_ces2020$race) == "character"
 class(cleaned_ces2020$region) == "character"
 class(cleaned_ces2020$employ) == "character"
 
-# range of data
-# voted_for
+# Range of data
+# Check range of data for voted_for  
 correct_voted_for <- 
   c("Trump", "Biden")
 
@@ -37,7 +38,7 @@ if (all(cleaned_ces2020$voted_for |>
 }
 
 
-# race
+# Check range of data for race
 correct_race <-
   c(
     "White",
@@ -59,7 +60,7 @@ if (all(cleaned_ces2020$race |>
 }
 
 
-# region
+# Check range of data for region
 correct_region <-
   c(
     "Northeast",
@@ -77,7 +78,7 @@ if (all(cleaned_ces2020$region |>
 }
 
 
-# employ
+# Check range of data for employ
 correct_employ <-
   c(
     "Full-time",

### 2024-03-07 paper/paper.qmd
added latex model

@@
   - Another author
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/hannahyu07/US-Election"
 date: today
@@
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+# analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+# 
+# analysis_data |> 
+#   ggplot(aes(x = width, y = length)) +
+#   geom_point(alpha = 0.8) +
+#   theme_minimal() +
+#   labs(x = "Wing width (mm)",
+#        y = "Wing length (mm)")
 ```
@@
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
+y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{race}_i + \beta_2 \times \mbox{region}_i + \beta_3 \times \mbox{employ}_i\\
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5)
 \end{align}
@@
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+# first_model <-
+#   readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
+# modelsummary::modelsummary(
+#   list(
+#     "First model" = first_model
+#   ),
+#   statistic = "mad",
+#   fmt = 2
+# )
 ```
@@
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+# 
+# pp_check(first_model) +
+#   theme_classic() +
+#   theme(legend.position = "bottom")
+# 
+# posterior_vs_prior(first_model) +
+#   theme_minimal() +
+#   scale_color_brewer(palette = "Set1") +
+#   theme(legend.position = "bottom") +
+#   coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
+# plot(first_model, "trace")
+# 
+# plot(first_model, "rhat")
 ```

### 2024-03-07 scripts/04-model.R
created model

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models
+# Author: 
+# Date: 07 March 2024
+# Contact: 
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
@@ -13,25 +13,47 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/analysis_data/cleaned_ces2020.csv")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# first_model <-
+#   stan_glm(
+#     formula = flying_time ~ length + width,
+#     data = analysis_data,
+#     family = gaussian(),
+#     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+#     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+#     prior_aux = exponential(rate = 1, autoscale = TRUE),
+#     seed = 853
+#   )
 
+# Convert variables to factors
+analysis_data$race <- factor(analysis_data$race)
+analysis_data$region <- factor(analysis_data$region)
+analysis_data$employ <- factor(analysis_data$employ)
+
+# Create voted_for variable in binary form
+analysis_data$voted_for_binary <- ifelse(analysis_data$voted_for == "Biden", 1, 0)
+
+#Model data
+set.seed(123)
+
+political_preferences <-
+  stan_glm(
+    voted_for_binary ~ race + region + employ,
+    data = analysis_data,
+    family = binomial(link = "logit"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = 
[…]

### 2024-03-08 paper/paper.qmd
ran model

@@
 library(here)
+library(rstanarm)
+library(modelsummary)
+
 ```
@@
 library(rstanarm)
+political_preferences <-
+  readRDS(file = here::here("models/political_preferences.rds"))
 
@@
 #| warning: false
+install.packages("modelsummary")
 
-# modelsummary::modelsummary(
-#   list(
-#     "First model" = first_model
-#   ),
-#   statistic = "mad",
-#   fmt = 2
-# )
+# Load the modelsummary package
+library(modelsummary)
+
+modelsummary(
+  list(
+    "Support Biden" = political_preferences
+  ),
+  statistic = "mad"
+  )
+
 ```

### 2024-03-08 scripts/04-model.R

@@ -15,18 +15,6 @@ library(rstanarm)
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/cleaned_ces2020.csv")
 
-### Model data ####
-# first_model <-
-#   stan_glm(
-#     formula = flying_time ~ length + width,
-#     data = analysis_data,
-#     family = gaussian(),
-#     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-#     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-#     prior_aux = exponential(rate = 1, autoscale = TRUE),
-#     seed = 853
-#   )
-
 # Convert variables to factors
 analysis_data$race <- factor(analysis_data$race)
 analysis_data$region <- factor(analysis_data$region)
@@ -35,7 +23,7 @@ analysis_data$employ <- factor(analysis_data$employ)
 # Create voted_for variable in binary form
 analysis_data$voted_for_binary <- ifelse(analysis_data$voted_for == "Biden", 1, 0)
 
-#Model data
+# Model data
 set.seed(123)
 
 political_preferences <-

### 2024-03-08 paper/paper.qmd
added graphs

@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-race_region
+#| fig-cap: The distribution of presidential preferences, by region and race
 #| echo: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
+ces2020 |>
+  ggplot(aes(x = race, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(region)) +
   theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+  labs(
+    x = "Race",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+```{r}
+#| label: fig-race_employ
+#| fig-cap: The distribution of presidential preferences, by region and employment status
+#| echo: false
+
+ces2020 |>
+  ggplot(aes(x = employ, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(region)) +
+  theme_minimal() +
+  labs(
+    x = "Employment status",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+```{r}
+#| label: fig-race_employ_white
+#| fig-cap: The distribution of presidential preferences, by region and employment status, only white people
+#| echo: false
+
+ces2020 |>
+  ggplot(aes(x = employ, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(region)) +
+  theme_minimal() +
+  labs(
+    x = "Employment status",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 ```

### 2024-03-08 paper/paper.qmd
add graph

@@
 
-ces2020 |>
+ces2020_selected_data <- ces2020[ces2020$race == "White", ]
+
+ces2020_selected_data |>
   ggplot(aes(x = employ, fill = voted_for)) +

### 2024-03-08 paper/paper.qmd
model (n=1000) and another graph

@@
 
-library(rstanarm)
 political_preferences <-
@@
 
-# first_model <-
-#   readRDS(file = here::here("models/first_model.rds"))
+political_preferences2 <-
+  readRDS(file = here::here("models/political_preferences2.rds"))
+
 ```
@@
 #| warning: false
-install.packages("modelsummary")
-
-# Load the modelsummary package
-library(modelsummary)
 
@@
 
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+modelsummary(
+  list(
+    "Support Biden" = political_preferences2
+  ),
+  statistic = "mad"
+  )
+
+```
+
+```{r}
+modelplot(political_preferences2, conf_level = 0.9) +
+  labs(x = "90 per cent credibility interval")
 ```

### 2024-03-08 scripts/04-model.R

@@ -43,5 +43,32 @@ saveRDS(
   file = "models/political_preferences.rds"
 )
 
+# Model 2 for n = 1000
+set.seed(123)
+
+ces2020_reduced <- 
+  analysis_data |> 
+  slice_sample(n = 1000)
+
+political_preferences2 <-
+  stan_glm(
+    voted_for_binary ~ race + region + employ,
+    data = ces2020_reduced,
+    family = binomial(link = "logit"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = 
+      normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 123
+  )
+
+saveRDS(
+  political_preferences2,
+  file = "models/political_preferences2.rds"
+)
 
 
+#### Save model ####
+saveRDS(
+  political_preferences2,
+  file = "models/political_preferences2.rds"
+)

### 2024-03-08 paper/paper.qmd
comment

@@
 #| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| label: tbl-modelresults1
+#| tbl-cap: "Explanatory models Political Preferences (n = 40000)"
 #| warning: false
@@
 #| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| label: tbl-modelresults2
+#| tbl-cap: ""Explanatory models Political Preferences (n = 1000)"
 #| warning: false

### 2024-03-08 scripts/04-model.R
tried 10 separate models cuz results are weird

@@ -67,8 +67,24 @@ saveRDS(
 )
 
 
+
+# Filter data to include only observations where region is "South"
+ces2020_reduced_south <- subset(analysis_data, region == "South")
+
+# Sample 1000 observations from the filtered dataset
+ces2020_reduced_south <- ces2020_reduced_south[sample(nrow(ces2020_reduced_south), 1000), ]
+
+# Fit logistic regression model using the filtered dataset
+political_preferences3 <- stan_glm(
+  voted_for_binary ~ race + employ,
+  data = ces2020_reduced_south,
+  family = binomial(link = "logit"),
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  seed = 123
+)
 #### Save model ####
 saveRDS(
-  political_preferences2,
-  file = "models/political_preferences2.rds"
+  political_preferences3,
+  file = "models/political_preferences3.rds"
 )

### 2024-03-08 paper/paper.qmd
^

@@
 
+political_preferences3 <-
+  readRDS(file = here::here("models/political_preferences3.rds"))
+
+political_preferences4 <-
+  readRDS(file = here::here("models/political_preferences4.rds"))
+
+political_preferences5 <-
+  readRDS(file = here::here("models/political_preferences5.rds"))
+
+political_preferences6 <-
+  readRDS(file = here::here("models/political_preferences6.rds"))
+
+political_preferences7 <-
+  readRDS(file = here::here("models/political_preferences7.rds"))
+
+political_preferences8 <-
+  readRDS(file = here::here("models/political_preferences8.rds"))
+
+political_preferences9 <-
+  readRDS(file = here::here("models/political_preferences9.rds"))
 ```
@@
 ```{r}
-modelplot(political_preferences2, conf_level = 0.9) +
+modelsummary(
+  list(
+    "Support Biden" = political_preferences3
+  ),
+  statistic = "mad"
+  )
+```
+
+```{r}
+modelsummary(
+  list(
+    "Support Biden" = political_preferences4
+  ),
+  statistic = "mad"
+  )
+```
+```{r}
+modelsummary(
+  list(
+    "Support Biden" = political_preferences5
+  ),
+  statistic = "mad"
+  )
+```
+```{r}
+modelsummary(
+  list(
+    "Support Biden" = political_preferences6
+  ),
+  statistic = "mad"
+  )
+```
+```{r}
+modelsummary(
+  list(
+    "Support Biden" = political_preferences7
+  ),
+  statistic = "mad"
+  )
+```
+```{r}
+modelsummary(
+  list(
+    "Support Biden" = political_preferences8
+  ),
+  statistic = "mad"
+  )
+```
+
+```{r}
+modelsummary(
+  list(
+    "Support Biden" = political_preferences9
+  ),
+  statistic = "mad"
+  )
+```
+
+```{r}
+modelplot(political_preferences9, conf_level = 0.9) +
   labs(x = "90 per cent credibility interval")

### 2024-03-08 scripts/04-model.R

@@ -88,3 +88,120 @@ saveRDS(
   political_preferences3,
   file = "models/political_preferences3.rds"
 )
+
+
+# Filter data to include only observations where region is "Northeast"
+ces2020_reduced_north <- subset(analysis_data, region == "Northeast")
+
+# Sample 1000 observations from the filtered dataset
+ces2020_reduced_north <- ces2020_reduced_north[sample(nrow(ces2020_reduced_north), 1000), ]
+
+# Fit logistic regression model using the filtered dataset
+political_preferences4 <- stan_glm(
+  voted_for_binary ~ race + employ,
+  data = ces2020_reduced_north,
+  family = binomial(link = "logit"),
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  seed = 123
+)
+#### Save model ####
+saveRDS(
+  political_preferences4,
+  file = "models/political_preferences4.rds"
+)
+
+
+# Filter data to include only observations where region is "West"
+ces2020_reduced_west <- subset(analysis_data, region == "West")
+
+# Sample 1000 observations from the filtered dataset
+ces2020_reduced_west <- ces2020_reduced_west[sample(nrow(ces2020_reduced_west), 1000), ]
+
+# Fit logistic regression model using the filtered dataset
+political_preferences5 <- stan_glm(
+  voted_for_binary ~ race + employ,
+  data = ces2020_reduced_west,
+  family = binomial(link = "logit"),
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  seed = 123
+)
+#### Save model ####
+saveRDS(
+  political_preferences5,
+  file = "models/political_preferences5.rds"
+)
+
+
+
+# Filter data to include only observations where region is "West"
+ces2020_reduced_black <- subset(analysis_data, race == "Black")
+
+# Sample 1000 observations from the filtered dataset
+ces2020_reduced_black <- ces2020_reduced_black[sample(nrow(ces2020_reduced_black), 1000), ]
+
+# Fit logistic regression model using the filtered dataset
+political_preferences6 <- stan_glm(
+  voted_for_binary ~ region + employ,
+  data = ces2020_reduced_black,
+  family = binomial(link = "logit"),
[…]

### 2024-03-08 paper/paper.qmd
deleted model 1 cuz runtime too long

@@
 
-political_preferences <-
-  readRDS(file = here::here("models/political_preferences.rds"))
-
 political_preferences2 <-
@@
   readRDS(file = here::here("models/political_preferences9.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults1
-#| tbl-cap: "Explanatory models Political Preferences (n = 40000)"
-#| warning: false
-
-modelsummary(
-  list(
-    "Support Biden" = political_preferences
-  ),
-  statistic = "mad"
-  )
-
 ```
@@
 ```
+
 ```{r}

### 2024-03-08 scripts/04-model.R

@@ -23,26 +23,6 @@ analysis_data$employ <- factor(analysis_data$employ)
 # Create voted_for variable in binary form
 analysis_data$voted_for_binary <- ifelse(analysis_data$voted_for == "Biden", 1, 0)
 
-# Model data
-set.seed(123)
-
-political_preferences <-
-  stan_glm(
-    voted_for_binary ~ race + region + employ,
-    data = analysis_data,
-    family = binomial(link = "logit"),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = 
-      normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 123
-  )
-
-#### Save model ####
-saveRDS(
-  political_preferences,
-  file = "models/political_preferences.rds"
-)
-
 # Model 2 for n = 1000
 set.seed(123)
 

### 2024-03-08 paper/paper.qmd
fixed up models and wrote model justification

--- 2024-03-08 paper/paper.qmd
@@
 library(modelsummary)
-
+library(ggplot2)
 ```
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between individuals of Black, Asian, and Hispanic ethnicities and support for Biden.
+This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall.
+These groups are more likely to align with Biden's policies, which prioritize inclusivity and diversity.
+White individuals with traditional family values and conservative leanings tend to support Trump.
+They are drawn to his emphasis on preserving traditional values and promises to uphold conservative principles, especially regarding immigration, law and order, and gun rights.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Conversely, we anticipate a negative relationship between voters in the South and Midwest regions and support for Biden.
+These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump.
+States such as Texas and Florida, which are known Republican strongholds, are located in the South.
+Therefore, individuals in these regions may be less inclined to support Biden's progressive agenda.
+
+Regarding employment status, we expect students, unemployed individuals, and those temporarily laid off to be more inclined to support Biden.
+Students are often exposed to diverse perspectives and progressive ideas in educational settings, making them more likely to endorse Biden's platform.
+Unemployed and laid-off individuals may favor Biden due to the Democratic Party's advocacy for social welfare programs and support for workers' rights.
+
+The voting behavior of employed individuals is harder to distinguish.
+Some working individuals support Trump due to their opposition to higher taxes and prefer his promises of tax cuts and economic deregulation.
+Conversely, others lean towards Biden because they believe tax increases should primarily target the wealthy and not burden the middle class.
+Additionally, educated and liberal-leaning working professionals may prioritize issues such as healthcare, climate change, and social justice, aligning them with Biden's platform.
 
@@
 #| message: false
+#|label: tbl-modelresults1
+#| tbl-cap: ""Explanatory models Political Preferences (n = 1000)"
 
-political_preferences <-
-  readRDS(file = here::here("models/political_preferences.rds"))
+political_preferences1 <-
+  readRDS(file = here::here("models/political_preferences1.rds"))
 
-political_preferences2 <-
-  readRDS(file = here::here("models/political_preferences2.rds"))
+modelsummary(
+  list(
+    "Support Biden" = political_preferences1
+  ),
+  statistic = "mad"
+  )
+```
+
+```{r}
+# Extract posterior samples
+posterior_samples <- as.matrix(political_preferences)
+
+# Calculate credible intervals (e.g., 95%)
+credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))
+
+# Extract coefficient names
+coefficient_names <- colnames(posterior_samples)
+
+# Create a data frame with coefficient names, coefficient estimates, and credible intervals
+table_data <- data.frame(
+  Posterior_Mean = colMeans(posterior_samples),
+  Credible_Interval_Lower = credible_intervals[1, ],
+  Credible_Interval_Upper = credible_intervals[2, ]
+)
+
+# Print the table
+print(table_data)
 
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults1
-#| tbl-cap: "Explanatory models Political Preferences (n = 40000)"
-#| warning: false
+modelplot(political_preferences1, conf_level = 0.9) +
+  labs(x = "90 per cent credibility interval")
+```
+```{r}
+# Create the model plot
+model_plot <- modelplot(political_preferences1, conf_level = 0.9)
 
-modelsummary(
-  list(
-    "Support Biden" = political_preferences
-  ),
-  statistic = "mad"
-  )
+# Modify the x-axis limits
+model_plot + xlim(-10, 10) +  # Adjust the limits as needed
+  labs(x = "90% Credibility Interval")
 
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults2
-#| tbl-cap: ""Explanatory models Political Preferences (n = 1000)"
-#| warning: false
-
-modelsummary(
-  list(
-    "Support Biden" = political_preferences2
-  ),
-  statistic = "mad"
-  )
-
-```
-
-```{r}
-modelplot(political_preferences2, conf_level = 0.9) +
-  labs(x = "90 per cent credibility interval")
 ```

### 2024-03-08 scripts/04-model.R

@@ -23,14 +23,14 @@ analysis_data$employ <- factor(analysis_data$employ)
 # Create voted_for variable in binary form
 analysis_data$voted_for_binary <- ifelse(analysis_data$voted_for == "Biden", 1, 0)
 
-# Model 2 for n = 1000
+# Model 1 for n = 1000
 set.seed(123)
 
 ces2020_reduced <- 
   analysis_data |> 
   slice_sample(n = 1000)
 
-political_preferences2 <-
+political_preferences1 <-
   stan_glm(
     voted_for_binary ~ race + region + employ,
     data = ces2020_reduced,
@@ -42,12 +42,12 @@ political_preferences2 <-
   )
 
 saveRDS(
-  political_preferences2,
-  file = "models/political_preferences2.rds"
+  political_preferences1,
+  file = "models/political_preferences1.rds"
 )
 
 
-
+# Model 2 for South
 # Filter data to include only observations where region is "South"
 ces2020_reduced_south <- subset(analysis_data, region == "South")
 
@@ -55,9 +55,32 @@ ces2020_reduced_south <- subset(analysis_data, region == "South")
 ces2020_reduced_south <- ces2020_reduced_south[sample(nrow(ces2020_reduced_south), 1000), ]
 
 # Fit logistic regression model using the filtered dataset
-political_preferences3 <- stan_glm(
+political_preferences2 <- stan_glm(
   voted_for_binary ~ race + employ,
   data = ces2020_reduced_south,
+  family = binomial(link = "logit"),
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  seed = 123
+)
+#### Save model ####
+saveRDS(
+  political_preferences2,
+  file = "models/political_preferences2.rds"
+)
+
+# Model 3 for Northeast
+
+# Filter data to include only observations where region is "Northeast"
+ces2020_reduced_north <- subset(analysis_data, region == "Northeast")
+
+# Sample 1000 observations from the filtered dataset
+ces2020_reduced_north <- ces2020_reduced_north[sample(nrow(ces2020_reduced_north), 1000), ]
+
+# Fit logistic regression model using the filtered dataset
+political_preferences3 <- stan_glm(
+  voted_for_binary ~ race + employ,
+  data = ces2020_reduced_north,
   family = binomial(link = "logit"),
[…]

### 2024-03-09 paper/paper.qmd
new addition

@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in
+
+[Appendix -@sec-model-details].
 
@@
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
 
@@
 #| message: false
-#|label: tbl-modelresults1
-#| tbl-cap: ""Explanatory models Political Preferences (n = 1000)"
+#| label: tbl-modelresults1
+#| tbl-cap: "Explanatory models Political Preferences (n = 1000)"
 
@@
   readRDS(file = here::here("models/political_preferences1.rds"))
+
+# Change variable names directly in the model object
+names(political_preferences1$coefficients) <- c(
+  "Intercept", "Black", "Hispanic", "Middle Eastern", "Native American", 
+  "Other race", "Two or more races", "White", "Northeast", "South", "West",
+  "Homemaker", "Other employment", "Part-time", "Permanently disabled", 
+  "Retired", "Student", "Temporarily laid off", "Unemployed"
+)
 
@@
 ```
+# need to be fixed
+Our results generally matches our justification. To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.
+
+The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.
+
+Black people's support for Biden is large.
+The estimated coefficient of 2.549 means that, holding all other variables constant, Black individuals are estimated to have a 2.549 unit increase in the log-odds of supporting Biden compared to the reference group.
+
+Hispanic races on average are also more likely to vote for Biden. (not significant)
+We observe an outlier race other which has a 37.999 higher log-odds of supporting Biden compared to the reference group.
+
+```{r}
+
+# Define the updated variable names
+new_coef_names <- c(
+  "Intercept", "Black", "Hispanic", "Middle Eastern", "Native American", 
+  "Other race", "Two or more races", "White", "Northeast", "South", "West",
+  "Homemaker", "Other employment", "Part-time", "Permanently disabled", 
+  "Retired", "Student", "Temporarily laid off", "Unemployed"
+)
+
+# Update variable names in the model object
+names(political_preferences1$coefficients) <- new_coef_names
+
+# Print the updated model summary
+print(
+  modelsummary(
+    list("Support Biden" = political_preferences1),
+    statistic = "mad"
+  )
+)
+
+```
+
+```{r}
+
+# Print the updated model summary with modified variable names
+print(
+  modelsummary(
+    list("Support Biden" = political_preferences1),
+    statistic = "mad",
+    coef_map = list(
+      Intercept = "Intercept",
+      raceBlack = "Black",
+      raceHispanic = "Hispanic",
+      raceMiddle_Eastern = "Middle Eastern",
+      raceNative_American = "Native American",
+      raceOther = "Other race",
+      `raceTwo or more races` = "Two or more races",
+      raceWhite = "White",
+      regionNortheast = "Northeast",
+      regionSouth = "South",
+      regionWest = "West",
+      employHomemaker = "Homemaker",
+      employOther = "Other employment",
+      employPart_time = "Part-time",
+      employPermanently_disabled = "Permanently disabled",
+      employRetired = "Retired",
+      employStudent = "Student",
+      `employTemporarily laid off` = "Temporarily laid off",
+      employUnemployed = "Unemployed"
+    )
+  )
+)
+
+```
 
@@
 # Extract posterior samples
-posterior_samples <- as.matrix(political_preferences)
-
-# Calculate credible intervals (e.g., 95%)
-credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))
-
-# Extract coefficient names
-coefficient_names <- colnames(posterior_samples)
-
-# Create a data frame with coefficient names, coefficient estimates, and credible intervals
-table_data <- data.frame(
-  Posterior_Mean = colMeans(posterior_samples),
-  Credible_Interval_Lower = credible_intervals[1, ],
-  Credible_Interval_Upper = credible_intervals[2, ]
-)
-
-# Print the table
-print(table_data)
+# posterior_samples <- as.matrix(political_preferences)
+# 
+# # Calculate credible intervals (e.g., 95%)
+# credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))
+# 
+# # Extract coefficient names
+# coefficient_names <- colnames(posterior_samples)
+# 
+# # Create a data frame with coefficient names, coefficient estimates, and credible intervals
+# table_data <- data.frame(
+#   Posterior_Mean = colMeans(posterior_samples),
+#   Credible_Interval_Lower = credible_intervals[1, ],
+#   Credible_Interval_Upper = credible_intervals[2, ]
+# )
+# 
+# # Print the table
+# print(table_data)
 
 ```
+Due to the fact that the credibility interval for race Other is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
+That's why we created a second plot with the x axis limited from -10 to 10.
 

### 2024-03-11 paper/paper.qmd
add subsections
added posterior predictive check for model result

@@
 library(ggplot2)
+library(knitr)
+library(marginaleffects)
 ```
@@
 
+## Estimand
+
 # Data {#sec-data}
+
+## Data Measurement
+
+## Summary Statistics
 
@@
 ```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-# analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-# 
-# analysis_data |> 
-#   ggplot(aes(x = width, y = length)) +
-#   geom_point(alpha = 0.8) +
-#   theme_minimal() +
-#   labs(x = "Wing width (mm)",
-#        y = "Wing length (mm)")
-```
-
-Talk way more about it.
 
@@
 ```
+```{r}
+# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
+
+pp_check(political_preferences1) +
+  theme(legend.position = "bottom")
+```
+```{r}
+
+# marginal effect -- ?
+
+slopes(political_preferences1) |>
+  summary() |>
+  select(-term) |>
+  kable(
+    col.names = c("Compare department", "Estimate", "2.5%", "97.5%"),
+    digits = 2, booktabs = TRUE, linesep = ""
+  )
+```
 

### 2024-03-11 paper/paper.qmd
organize the structure

@@
 
+# Model
+
+The goal of our modelling strategy is twofold. Firstly,...
+
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in
+
+[Appendix -@sec-model-details].
+
+## Model set-up
+
+Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+
+\begin{align} 
+y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{race}_i + \beta_2 \times \mbox{region}_i + \beta_3 \times \mbox{employ}_i\\
+\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5)
+\end{align}
+
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
+
+### Model justification
+
+We expect a positive relationship between individuals of Black, Asian, and Hispanic ethnicities and support for Biden.
+This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall.
+These groups are more likely to align with Biden's policies, which prioritize inclusivity and diversity.
+White individuals with traditional family values and conservative leanings tend to support Trump.
+They are drawn to his emphasis on preserving traditional values and promises to uphold conservative principles, especially regarding immigration, law and order, and gun rights.
+
+Conversely, we anticipate a negative relationship between voters in the South and Midwest regions and support for Biden.
+These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump.
+States such as Texas and Florida, which are known Republican strongholds, are located in the South.
+Therefore, individuals in these regions may be less inclined to support Biden's progressive agenda.
+
+Regarding employment status, we expect students, unemployed individuals, and those temporarily laid off to be more inclined to support Biden.
+Students are often exposed to diverse perspectives and progressive ideas in educational settings, making them more likely to endorse Biden's platform.
+Unemployed and laid-off individuals may favor Biden due to the Democratic Party's advocacy for social welfare programs and support for workers' rights.
+
+The voting behavior of employed individuals is harder to distinguish.
+Some working individuals support Trump due to their opposition to higher taxes and prefer his promises of tax cuts and economic deregulation.
+Conversely, others lean towards Biden because they believe tax increases should primarily target the wealthy and not burden the middle class.
+Additionally, educated and liberal-leaning working professionals may prioritize issues such as healthcare, climate change, and social justice, aligning them with Biden's platform.
+
+-------------------------------needs some explanation
+```{r}
+# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
+
+pp_check(political_preferences1) +
+  theme(legend.position = "bottom")
+```
+
 ```{r}
@@
 
-# Model
+```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
+# get state by state proportions for our polling data
+polling_props <- polling %>% 
+  group_by(stateicp, vote_biden) %>% 
+  summarise(n = n()) %>% 
+  mutate(prop = n/sum(n))
 
-The goal of our modelling strategy is twofold. Firstly,...
+# combine the polling data proportions with the post-stratification data
+poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
+poll_post_biden <- poll_post_biden %>% 
+  filter(vote_biden == 1)
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in
+# plot for predictions
 
-[Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{race}_i + \beta_2 \times \mbox{region}_i + \beta_3 \times \mbox{employ}_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_2 &\sim \mbox{Normal}(0, 2.5)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
-
-### Model justification
-
-We expect a positive relationship between individuals of Black, Asian, and Hispanic ethnicities and support for Biden.
-This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall.
-These groups are more likely to align with Biden's policies, which prioritize inclusivity and diversity.
-White individuals with traditional family values and conservative leanings tend to support Trump.
-They are drawn to his emphasis on preserving traditional values and promises to uphold conservative principles, especially regarding immigration, law and order, and gun rights.
-
-Conversely, we anticipate a negative relationship between voters in the South and Midwest regions and support for Biden.
-These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump.
-States such as Texas and Florida, which are known Republican strongholds, are located in the South.
-Therefore, individuals in these regions may be less inclined to support Biden's progressive agenda.
-
-Regarding employment status, we expect students, unemployed individuals, and those temporarily laid off to be more inclined to support Biden.
-Students are often exposed to diverse perspectives and progressive ideas in educational settings, making them more likely to endorse Biden's platform.
-Unemployed and laid-off individuals may favor Biden due to the Democratic Party's advocacy for social welfare programs and support for workers' rights.
-
-The voting behavior of employed individuals is harder to distinguish.
-Some working individuals support Trump due to their opposition to higher taxes and prefer his promises of tax cuts and economic deregulation.
-Conversely, others lean towards Biden because they believe tax increases should primarily target the wealthy and not burden the middle class.
-Additionally, educated and liberal-leaning working professionals may prioritize issues such as healthcare, climate change, and social justice, aligning them with Biden's platform.
+poll_post_biden %>% 
+  ggplot(aes(x = stateicp, y = biden_predict)) +
+  geom_point(aes(color = "black")) +
+  geom_line(aes(group = 1)) +
+  scale_y_continuous(labels = scales::percent) +
+  theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
+  geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
+              alpha = 0.2, fill = "red") +
+  geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
+            linetype = "twodash") +
+  geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
+  geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
+  scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
+  labs(title = "Proportion of People voting for Joe Biden by State",
+       x = "State", y = "Percentage Voting Biden")
+```
 
@@
 ```
-```{r}
-# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
-
-pp_check(political_preferences1) +
-  theme(legend.position = "bottom")
-```
-```{r}
-
-# marginal effect -- ?
-
-slopes(political_preferences1) |>
-  summary() |>
-  select(-term) |>
-  kable(
-    col.names = c("Compare department", "Estimate", "2.5%", "97.5%"),
-    digits = 2, booktabs = TRUE, linesep = ""
-  )
-```
 

### 2024-03-11 paper/paper.qmd
change structure
added result section

@@
 
+# Results
+
+## Data Result
+@fig-race_region shows the relationship between race, region, and voting preference.
+In the Northeast, Midwest, and West regions of the United States, there is a consistent pattern where individuals across various racial groups tend to show greater support for Biden over Trump.
+Conversely, in the South, there is a distinct divide, with White individuals predominantly favoring Trump, while almost all other racial groups support Biden more than Trump.
+Overall, the four subplots all illustrate that among Black, Asian, and Hispanic communities, the proportion of support for Biden exceeds that for Trump.
+However, it is evident that White individuals constitute a significantly larger portion of the population compared to other racial groups, thereby exerting a greater influence on voting outcomes.
 ```{r}
@@
 ```
+@fig-race_employ illustrates the relationship between region, employment status, and voting preferences for Trump and Biden.
+Across all regions, people in full-time and part-time employment show a greater percentage of support for Biden than to Trump.
+Yet, among retired people, support for Trump and Biden is roughly comparable: with a slight tilt towards Biden in the Northeast, Midwest, and West, and towards Trump in the South.
+In addition, people with other employment statuses generally favor Biden over Trump, except for certain groups in the South.
+
 ```{r}
@@
 
+```{r}
+library(plotly)
+plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("blue", "red")) %>% 
+  add_markers(color = ces2020$voted_for, opacity = 0.1)
+```
+
+```{r prediction, echo=F, warning=F, message=F}
+
+# generate predictions for each of our grouped cells
+props$estimate <- predict.glm(political_preferences1, newdata = props,
+                          type = "response")
+
+# create a new column with number of voters from each cell voting Biden
+props <- props %>% mutate(num_voters = n*estimate)
+
+# get errors for our prediction
+errors <- predict.glm(model, newdata = props,
+                      type = "response", se.fit = T)
+lower <- errors$fit - errors$se.fit
+upper <- errors$fit + errors$se.fit
+
+# combine the proportions and the errors we generated
+props_error <- cbind(props, lower, upper)
+props_error <- props_error %>% 
+  rename("lower" = ...11,
+         "upper" = ...12)
+
+# create a new column with number of voters from each cell voting Biden
+props_error <- props_error %>% mutate(num_voters_lower = n*lower,
+                                num_voters_upper = n*upper)
+
+# create a new dataset which contains upper and lower estimates for proportions
+# of votes for each state
+voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
+                                       biden_predict_prop_lower = lower*prop,
+                                       biden_predict_prop_upper = upper*prop) %>%
+  group_by(stateicp) %>%
+  summarise(biden_predict = sum(biden_predict_prop),
+            biden_predict_lower = sum(biden_predict_prop_lower),
+            biden_predict_upper = sum(biden_predict_prop_upper))
+```
+
 ```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
@@
 poll_post_biden %>% 
-  ggplot(aes(x = stateicp, y = biden_predict)) +
+  ggplot(aes(x = employ, y = biden_predict)) +
   geom_point(aes(color = "black")) +
@@
 ```
-
-# Results
 

### 2024-03-11 paper/paper.qmd
modell

--- 2024-03-11 paper/paper.qmd
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+In our analysis, we utilized a Bayesian logistic regression model to examine the relationship between voter preferences and various demographic and socioeconomic factors.
+The model is formulated as follows:
 
@@
 \end{align}
+
+In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted for a particular candidate (e.g., Biden or Trump).
+The probability of voting for the candidate ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$)) corresponding to the predictor variables race, region, and employment status, respectively.
+These predictor variables are denoted as \text{race}_i, \text{region}_i, and \text{employ}_i, where $i$ indexes the individuals in the dataset.
+
+The intercept ($\alpha$) and coefficients ($\beta_1$, $\beta_2$, $\beta_3$) are assigned informative prior distributions to regularize the model.
+Specifically, we assume a normal distribution with a mean of 0 and a standard deviation of 2.5 for each parameter.
+
+We chose this modeling approach for several reasons.
+Firstly, logistic regression is well-suited for binary outcome variables, making it appropriate for analyzing voting behavior.
+Additionally, Bayesian methods allow us to incorporate prior knowledge and uncertainty into our analysis, providing more robust estimates of the model parameters.
+
+Alternative modeling approaches, such as machine learning algorithms, were also considered.
+However, we chose Bayesian logistic regression for its flexibility, interpretability, and ability to handle uncertainty.
 
@@
 
+# Results
 ```{r}
@@
 
-# Results
-
 Our results are summarized in @tbl-modelresults.
@@
     statistic = "mad"
-  )
-)
-
-```
-
-```{r}
-
-# Print the updated model summary with modified variable names
-print(
-  modelsummary(
-    list("Support Biden" = political_preferences1),
-    statistic = "mad",
-    coef_map = list(
-      Intercept = "Intercept",
-      raceBlack = "Black",
-      raceHispanic = "Hispanic",
-      raceMiddle_Eastern = "Middle Eastern",
-      raceNative_American = "Native American",
-      raceOther = "Other race",
-      `raceTwo or more races` = "Two or more races",
-      raceWhite = "White",
-      regionNortheast = "Northeast",
-      regionSouth = "South",
-      regionWest = "West",
-      employHomemaker = "Homemaker",
-      employOther = "Other employment",
-      employPart_time = "Part-time",
-      employPermanently_disabled = "Permanently disabled",
-      employRetired = "Retired",
-      employStudent = "Student",
-      `employTemporarily laid off` = "Temporarily laid off",
-      employUnemployed = "Unemployed"
-    )
   )

### 2024-03-11 scripts/04-model.R

@@ -1,11 +1,12 @@
 #### Preamble ####
 # Purpose: Models
-# Author: 
+# Author: Hannah Yu
 # Date: 07 March 2024
-# Contact: 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: run 01-download_data.R and 02-data_cleaning.R first to 
+# get the cleaned dataset
+# Any other information needed?
 
 
 #### Workspace setup ####

### 2024-03-11 paper/paper.qmd

--- 2024-03-11 paper/paper.qmd
@@
 ```{r}
-
-# Print the updated model summary with modified variable names
-print(
-  modelsummary(
-    list("Support Biden" = political_preferences1),
-    statistic = "mad",
-    coef_map = list(
-      Intercept = "Intercept",
-      raceBlack = "Black",
-      raceHispanic = "Hispanic",
-      raceMiddle_Eastern = "Middle Eastern",
-      raceNative_American = "Native American",
-      raceOther = "Other race",
-      `raceTwo or more races` = "Two or more races",
-      raceWhite = "White",
-      regionNortheast = "Northeast",
-      regionSouth = "South",
-      regionWest = "West",
-      employHomemaker = "Homemaker",
-      employOther = "Other employment",
-      employPart_time = "Part-time",
-      employPermanently_disabled = "Permanently disabled",
-      employRetired = "Retired",
-      employStudent = "Student",
-      `employTemporarily laid off` = "Temporarily laid off",
-      employUnemployed = "Unemployed"
-    )
-  )
-)
-
-```
-
-```{r}
 # Extract posterior samples

### 2024-03-11 paper/paper.qmd
added introduction, results

--- 2024-03-11 paper/paper.qmd
@@
 library(marginaleffects)
+library(plotly)
 ```
@@
 # Introduction
+Three years ago, the United States once again was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
+The Democratic and Repulican parties are represented by Donald Trump and Joe Biden respectively.
+Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
+His winning was surprising and it led people to challenge the preconceived notions and reliability of pre-election polling data [citation needed].
+On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign [citation needed].
+He aimed to regain control from the Repulican party.
+In the end, Biden won the election by 51.3% majority votes [citation needed].
+It is important for us to understand how various demographic, economic, and social factors may influence individuals' voting decisions, which is why we decide to analyze the 2020 election dataset and build a prediction model.
+This allows us to discover trends and address potential issues in society to better reflect the needs and preferences of diverse communities.
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+In our analysis, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study (CES)  [citation needed].
+Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
+Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES dataset, which are race, region that they live, and employment status.
 
-The remainder of this paper is structured as follows. @sec-data....
+Our report consists of four sections, not including the introduction.
+In Section 2, we look at the data we used for our report and include some tables and graphs to illustrate the different groups of people in our data.
+In section 3, we build the model and discuss its justification and explanation.
+The results of our predictions is highlighted in the Section 4 using tables and graphs.
+Lastly, discussions are conducted based on
+the findings, which addresses the voting prediction results based on race, region, and employment status.
+In this report, R statistical programming language is used, with R packages: [a lot of citations needed]
 
@@
 ```
+# ```{r}
+# #| label: fig-race_employ_white
+# #| fig-cap: The distribution of presidential preferences, by region and employment status, only white people
+# #| echo: false
+# 
+# ces2020_selected_data <- ces2020[ces2020$race == "White", ]
+# 
+# ces2020_selected_data |>
+#   ggplot(aes(x = employ, fill = voted_for)) +
+#   stat_count(position = "dodge") +
+#   facet_wrap(facets = vars(region)) +
+#   theme_minimal() +
+#   labs(
+#     x = "Employment status",
+#     y = "Number of respondents",
+#     fill = "Voted for"
+#   ) +
+#   coord_flip() +
+#   scale_fill_brewer(palette = "Set1") +
+#   theme(legend.position = "bottom")
+# ```
+
 ```{r}
-#| label: fig-race_employ_white
-#| fig-cap: The distribution of presidential preferences, by region and employment status, only white people
+#| label: fig-race_employ_region
+#| fig-cap: The distribution of presidential preferences, by race, region and employment status
 #| echo: false
 
-ces2020_selected_data <- ces2020[ces2020$race == "White", ]
-
-ces2020_selected_data |>
-  ggplot(aes(x = employ, fill = voted_for)) +
-  stat_count(position = "dodge") +
-  facet_wrap(facets = vars(region)) +
-  theme_minimal() +
-  labs(
-    x = "Employment status",
-    y = "Number of respondents",
-    fill = "Voted for"
-  ) +
-  coord_flip() +
-  scale_fill_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
-```
-
-```{r}
-library(plotly)
 plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("blue", "red")) %>% 
@@
 ```
+
+## Model Results
 

### 2024-03-11 paper/paper.qmd
update intro

@@
 # Introduction
-Three years ago, the United States once again was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
-The Democratic and Repulican parties are represented by Donald Trump and Joe Biden respectively.
+Four years ago, the United States once again was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
+The Democratic and Republican parties are represented by Donald Trump and Joe Biden respectively.
 Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
@@
 On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign [citation needed].
-He aimed to regain control from the Repulican party.
+He aimed to regain control from the Republican party.
 In the end, Biden won the election by 51.3% majority votes [citation needed].
-It is important for us to understand how various demographic, economic, and social factors may influence individuals' voting decisions, which is why we decide to analyze the 2020 election dataset and build a prediction model.
+It is important for us to understand how various demographic, economic, and social factors may influence individuals' voting decisions, which is why we decide to analyze the 2020 election data set and build a prediction model.
 This allows us to discover trends and address potential issues in society to better reflect the needs and preferences of diverse communities.
 
-In our analysis, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study (CES)  [citation needed].
+In this paper, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study (CES)  [citation needed].
 Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
-Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES dataset, which are race, region that they live, and employment status.
+Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set, which are race, region that they live, and employment status.
 
-Our report consists of four sections, not including the introduction.
-In Section 2, we look at the data we used for our report and include some tables and graphs to illustrate the different groups of people in our data.
+**add： 4) what was done; 5) what was found after we finish the results section
+
+This report consists of four sections, not including the introduction.
+In Section 2, we look at the data used for our report and include some tables and graphs to illustrate the different groups of people in our data.
 In section 3, we build the model and discuss its justification and explanation.
@@
 the findings, which addresses the voting prediction results based on race, region, and employment status.
+
 In this report, R statistical programming language is used, with R packages: [a lot of citations needed]

### 2024-03-11 paper/paper.qmd
some edits

@@
 The results of our predictions is highlighted in the Section 4 using tables and graphs.
-Lastly, discussions are conducted based on
-the findings, which addresses the voting prediction results based on race, region, and employment status.
+Lastly, discussions are conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.
 
@@
 
-To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
+To avoid excessive runtime, we randomly sampled 1000 observations to fit the model.
 
@@
 @fig-race_region shows the relationship between race, region, and voting preference.
-In the Northeast, Midwest, and West regions of the United States, there is a consistent pattern where individuals across various racial groups tend to show greater support for Biden over Trump.
+In the Northeast, Midwest, and West regions of the United States, there is a consistent pattern where individuals across almost all racial groups tend to show greater support for Biden over Trump.
 Conversely, in the South, there is a distinct divide, with White individuals predominantly favoring Trump, while almost all other racial groups support Biden more than Trump.
@@
 Across all regions, people in full-time and part-time employment show a greater percentage of support for Biden than to Trump.
-Yet, among retired people, support for Trump and Biden is roughly comparable: with a slight tilt towards Biden in the Northeast, Midwest, and West, and towards Trump in the South.
-In addition, people with other employment statuses generally favor Biden over Trump, except for certain groups in the South.
+Among retired people, support for Trump and Biden is roughly comparable: with a slight tilt towards Biden in the Northeast, Midwest, and West, and towards Trump in the South.
+In addition, people with other employment statuses generally favor Biden over Trump, except for certain group (Homemaker) in the South.
 
@@
 
+This bubble plot illustrates four variables: race, region, employment status, and voting preference.
+Darker dots indicate a higher number of people, with red representing Trump supporters and blue for Biden supporters.
+Purple dots suggest similar support rates for both candidates, since blue and red makes purple in a 1:1 ratio.
+We can see that the darker dots are mostly in White, Black, Hispanic communities for full-time, part-time, or retired individuals.
+The darker dots are all blue, which indicates stronger support for Biden.
+It can also be noted that there are very few entirely red dots, which means that there is no significant disparities in voting percentages between Trump and Biden even among those groups which partially supported Trump.
+In those purple dots, we found that mostly are from people who are either Native American or from the South.
 ```{r}
@@
 
-plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("blue", "red")) %>% 
-  add_markers(color = ces2020$voted_for, opacity = 0.1)
+plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("red", "blue")) %>% 
+  add_markers(color = ces2020$voted_for, opacity = 0.03, size = 0.4) %>%
+  layout(xaxis = list(title = 'Race'), yaxis = list(title = 'Region'), zaxis = list(title = 'Employment Status')) %>%
+  layout(xaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
+         yaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
+         zaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)))
 ```

### 2024-03-11 paper/paper.qmd
test model, model explanatin, new tables and checks

--- 2024-03-11 paper/paper.qmd
@@
 library(plotly)
+library(tibble)
+library(margins)
+
 ```
@@
 # Introduction
-Three years ago, the United States once again was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
-The Democratic and Repulican parties are represented by Donald Trump and Joe Biden respectively.
-Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
-His winning was surprising and it led people to challenge the preconceived notions and reliability of pre-election polling data [citation needed].
-On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign [citation needed].
-He aimed to regain control from the Repulican party.
-In the end, Biden won the election by 51.3% majority votes [citation needed].
-It is important for us to understand how various demographic, economic, and social factors may influence individuals' voting decisions, which is why we decide to analyze the 2020 election dataset and build a prediction model.
-This allows us to discover trends and address potential issues in society to better reflect the needs and preferences of diverse communities.
 
-In our analysis, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study (CES)  [citation needed].
-Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
-Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES dataset, which are race, region that they live, and employment status.
+You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
 
-Our report consists of four sections, not including the introduction.
-In Section 2, we look at the data we used for our report and include some tables and graphs to illustrate the different groups of people in our data.
-In section 3, we build the model and discuss its justification and explanation.
-The results of our predictions is highlighted in the Section 4 using tables and graphs.
-Lastly, discussions are conducted based on
-the findings, which addresses the voting prediction results based on race, region, and employment status.
-In this report, R statistical programming language is used, with R packages: [a lot of citations needed]
+The remainder of this paper is structured as follows. @sec-data....
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm.
+We use the default priors from `rstanarm`.
+Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters.
+To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix A).
 
@@
 ```
-# ```{r}
-# #| label: fig-race_employ_white
-# #| fig-cap: The distribution of presidential preferences, by region and employment status, only white people
-# #| echo: false
-# 
-# ces2020_selected_data <- ces2020[ces2020$race == "White", ]
-# 
-# ces2020_selected_data |>
-#   ggplot(aes(x = employ, fill = voted_for)) +
-#   stat_count(position = "dodge") +
-#   facet_wrap(facets = vars(region)) +
-#   theme_minimal() +
-#   labs(
-#     x = "Employment status",
-#     y = "Number of respondents",
-#     fill = "Voted for"
-#   ) +
-#   coord_flip() +
-#   scale_fill_brewer(palette = "Set1") +
-#   theme(legend.position = "bottom")
-# ```
+```{r}
+#| label: fig-race_employ_white
+#| fig-cap: The distribution of presidential preferences, by region and employment status, only white people
+#| echo: false
+
+ces2020_selected_data <- ces2020[ces2020$race == "White", ]
+
+ces2020_selected_data |>
+  ggplot(aes(x = employ, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(region)) +
+  theme_minimal() +
+  labs(
+    x = "Employment status",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
 
 ```{r}
-#| label: fig-race_employ_region
-#| fig-cap: The distribution of presidential preferences, by race, region and employment status
-#| echo: false
-
+library(plotly)
 plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("blue", "red")) %>% 
@@
 ```
-
-## Model Results
 
@@
 ```{r}
+
+# Marginal Effect 
+political_preferences_predictions <- predictions(political_preferences1) |>
+  as_tibble()
+
+political_preferences_predictions
+
+```
+
+```{r}
+library(margins)
+
+# Marginal effects for each predictor variable
+marginal_effects <- margins(political_preferences1)
+
+# Plotting marginal effects for race
+race_effects <- dyplot(marginal_effects, variables = "race")
+race_effects
+
+# Plotting marginal effects for region
+region_effects <- dyplot(marginal_effects, variables = "region")
+region_effects
+
+# Plotting marginal effects for employ
+employ_effects <- dyplot(marginal_effects, variables = "employ")
+employ_effects
+
+```
+
+```{r}
 #| echo: false
@@
 ```{r}
+# Load required libraries
+library(bayestestR)
 
-# Define the updated variable names
-new_coef_names <- c(
-  "Intercept", "Black", "Hispanic", "Middle Eastern", "Native American", 
-  "Other race", "Two or more races", "White", "Northeast", "South", "West",
-  "Homemaker", "Other employment", "Part-time", "Permanently disabled", 
-  "Retired", "Student", "Temporarily laid off", "Unemployed"
-)
+# Extract posterior draws from the model object
+posterior_draws <- as.matrix(political_preferences1)
 
-# Update variable names in the model object
-names(political_preferences1$coefficients) <- new_coef_names
+# Define the predictor variables for which you want to compute marginal effects
+predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
+                         "Other race", "Two or more races", "White", "Northeast", 
+                         "South", "West", "Homemaker", "Other employment", 
+                         "Part-time", "Permanently disabled", "Retired", 
+                         "Student", "Temporarily laid off", "Unemployed")
 
-# Print the updated model summary
-print(
-  modelsummary(
-    list("Support Biden" = political_preferences1),
-    statistic = "mad"
-  )
-)
+# Compute marginal effects
+marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
+
+# Summary of marginal effects
+summary(marginal_effects)
+
+```
+
+```{r}
+library(tidybayes)
+
+# Extract draws from the Bayesian model
+draws <- spread_draws(political_preferences1)
+
+# Plot the posterior distribution of a predictor variable
+ggplot(draws, aes(x = raceBlack)) +
+  geom_density(fill = "skyblue", color = "black") +
+  labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
 
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Second discussion point
 
-## Second discussion point
+We observe
 

### 2024-03-11 scripts/03-test_data.R

@@ -99,3 +99,4 @@ if (all(cleaned_ces2020$employ |>
 } else {
   "Not all of the employ have been cleaned completely"
 }
+

### 2024-03-11 scripts/05-test_model.R

@@ -1,0 +1,29 @@
+#### Preamble ####
+# Purpose: Tests the model
+# Author: Hannah Yu
+# Date: 06 March 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# License: --
+# Pre-requisites: run 04-model.R to get model
+
+
+# Check the class of the model object
+if ("stanreg" %in% class(political_preferences1) || "glm" %in% class(political_preferences1) || "lm" %in% class(political_preferences1)) {
+  "The class of political_preferences1 is as expected."
+} else {
+  "The class of political_preferences1 is not as expected."
+}
+# Get the number of observations
+if (!is.null(political_preferences1$data)) {
+  if (nrow(political_preferences1$data) == 1000) {
+    "The number of observations is 1000."
+  } else {
+    "The number of observations is not 1000."
+  }
+} else {
+  "The number of observations is not available."
+}
+
+
+# Check the coefficients of the model 
+summary(political_preferences1)

### 2024-03-11 paper/paper.qmd
explained model and credble interval, and weakness

--- 2024-03-11 paper/paper.qmd
@@
 
-In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted for a particular candidate (e.g., Biden or Trump).
-The probability of voting for the candidate ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$)) corresponding to the predictor variables race, region, and employment status, respectively.
+In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump).
+The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$)) corresponding to the predictor variables race, region, and employment status, respectively.
 These predictor variables are denoted as \text{race}_i, \text{region}_i, and \text{employ}_i, where $i$ indexes the individuals in the dataset.
@@
 
-Alternative modeling approaches, such as machine learning algorithms, were also considered.
-However, we chose Bayesian logistic regression for its flexibility, interpretability, and ability to handle uncertainty.
+Alternative modeling approaches, such as linear regression models, were also considered. However, we chose Bayesian logistic regression because our result is a binary variable of voter's decision.
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-To avoid excessive runtime, we randomly sampled 1000 observations to fit the model.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm.
+We use the default priors from `rstanarm`.
+Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters.
+To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix A).
 
@@
 ```
-# ```{r}
+
+```{r}
 # #| label: fig-race_employ_white
@@
 #   theme(legend.position = "bottom")
-# ```
+```
 
@@
 ```
-# need to be fixed
-Our results generally matches our justification. To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.
-
-The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+Our results generally matches our justification.
+To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
 In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.
 
-Black people's support for Biden is large.
-The estimated coefficient of 2.549 means that, holding all other variables constant, Black individuals are estimated to have a 2.549 unit increase in the log-odds of supporting Biden compared to the reference group.
+Black individual's support for Biden is large.
+The estimated coefficient of 2.549 suggests that, holding all other variables constant, Black individuals are estimated to have a 2.549 unit increase in the log-odds of supporting Biden compared to the reference group.
+Hispanic races on average are also more likely to vote for Biden.
+We observe an outlier, individuals with race "other" has a 37.999 higher log-odds of supporting Biden compared to the reference group.
 
-Hispanic races on average are also more likely to vote for Biden. (not significant)
-We observe an outlier race other which has a 37.999 higher log-odds of supporting Biden compared to the reference group.
+Voters preference for candidates also vary by regions and their employment status.
+Biden has more supports in the Northeast and West region while Trump gains a majority of his votes from the South.
+As anticipated, students exhibit strong support for Biden.
+Additionally, individuals who are laid off, unemployed, or employed part-time, potentially reliant on social benefits, also prefer for Biden.
 
 ```{r}
+# Load required libraries
+library(bayestestR)
 
-# Define the updated variable names
-new_coef_names <- c(
-  "Intercept", "Black", "Hispanic", "Middle Eastern", "Native American", 
-  "Other race", "Two or more races", "White", "Northeast", "South", "West",
-  "Homemaker", "Other employment", "Part-time", "Permanently disabled", 
-  "Retired", "Student", "Temporarily laid off", "Unemployed"
-)
+# Extract posterior draws from the model object
+posterior_draws <- as.matrix(political_preferences1)
 
-# Update variable names in the model object
-names(political_preferences1$coefficients) <- new_coef_names
+# Define the predictor variables for which you want to compute marginal effects
+predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
+                         "Other race", "Two or more races", "White", "Northeast", 
+                         "South", "West", "Homemaker", "Other employment", 
+                         "Part-time", "Permanently disabled", "Retired", 
+                         "Student", "Temporarily laid off", "Unemployed")
 
-# Print the updated model summary
-print(
-  modelsummary(
-    list("Support Biden" = political_preferences1),
-    statistic = "mad"
-  )
-)
+# Compute marginal effects
+marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
+
+# Summary of marginal effects
+summary(marginal_effects)
+
+```
+
+```{r}
+library(tidybayes)
+
+# Extract draws from the Bayesian model
+draws <- spread_draws(political_preferences1)
+
+# Plot the posterior distribution of a predictor variable
+ggplot(draws, aes(x = raceBlack)) +
+  geom_density(fill = "skyblue", color = "black") +
+  labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
 
@@
 ```
-Due to the fact that the credibility interval for race Other is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
-That's why we created a second plot with the x axis limited from -10 to 10.
+
+Figure # shows range of coefficient estimates of our model within the 90% probability.
+Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
+Therefore we created figure # with the x axis limited from -10 to 10.
+
+Combing figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+The estimates are significant if the intervals do not cross 0.
+The value for the estimates are in log-odds, indicating that if the interval is positive, the individual supports Biden, if negative, the individual supports Trump.
 
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of support for Biden 1"
+
 modelplot(political_preferences1, conf_level = 0.9) +
-  labs(x = "90 per cent credibility interval")
+  labs(x = "90% credibility interval")
 ```
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of support for Biden 1"
 # Create the model plot
@@
 # Modify the x-axis limits
-model_plot + xlim(-10, 10) +  # Adjust the limits as needed
+model_plot + xlim(-5, 5) +  # Adjust the limits as needed
   labs(x = "90% Credibility Interval")
@@
 
-Weaknesses and next steps should also be included.
+add more weakness about the data, graphs, etc.
+
+One weakness of using a logistic regression model is its inability to predict voting turnout for candidates beyond the Biden or Trump.
+Expanding the analysis to include other candidates would enhance its comprehensiveness.
+Furthermore, the reliability of our findings is contingent upon the accuracy of the survey data.
+Respondents may provide inaccurate or misleading information, intentionally or unintentionally, leading to biased estimates and unreliable predictions.
+Additionally, missing data (N/As) can introduce further challenges, as logistic regression requires complete data for accurate modeling.
 

### 2024-03-11 paper/paper.qmd
region discussion

@@
 The estimates are significant if the intervals do not cross 0.
-The value for the estimates are in log-odds, indicating that if the interval is positive, the individual supports Biden, if negative, the individual supports Trump.
+The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
 
@@
 
+maybe talk about race?
+
 ## Second discussion point
 
-We observe
+Our analysis highlights regional voting variations, with the Northeast, West, and Midwest favoring Biden, while the South supports Trump.
+These differences stem from diverse cultural, family, religious, and social perspectives.
+
+Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes.
+This support is particularly evident in notable cities within these regions, driven by various factors including liberal ideals and progressive policies.
+For instance, states like New York and Massachusetts support Biden due to their liberal-leaning populations, diverse demographics, and emphasis on social justices.
+Similarly, on the West Coast, states such as California and Washington are known for their progressive values and advocacy for issues like environmental conservation and LGBTQ+ rights, contributing to Biden's popularity in these areas.
+In the Southwest, states like Arizona and Nevada, with growing minority populations and concerns over immigration policies, also show significant support for Biden.
+Additionally, states around the Great Lakes, including Illinois and Michigan, align with Biden's platform due to their industrial heritage and strong labor unions.
+
+Voters favoring Biden are predominantly concentrated in big cities and large suburban regions, whereas Trump supporters are dispersed across rural areas with lower population density.
+Consequently, Trump secured victories in 2,588 counties, whereas Biden won over just 551 [@frey_2021].
+Even in traditionally Republican states, major urban areas exhibit significant support for Biden.
+Notable examples include Charlotte, North Carolina; Salt Lake City, Utah; and Nashville and Memphis, Tennessee, among others [@cnn_2020].
+
+This trend reflects the impact of diverse demographics, progressive ideologies, and evolving societal norms in urban areas.
+Here, a mix of cultural diversity, acceptance of progressive values, and socio-economic factors favors Biden's platform.
+Additionally, urban centers, with their concentration of educational and cultural institutions, often align with Democratic policies on healthcare, climate change, and social justice.
+
+The 2020 election witnessed intriguing shifts in traditionally conservative states, turning them into battlegrounds.
+For instance, Texas, a Republican stronghold, saw unprecedented Democratic gains, though ultimately remaining red.
+Notably, the five largest cities in Texas—Houston, San Antonio, Dallas, Austin, and Fort Worth—all backed the Democratic party, marking a significant departure from historical voting patterns [@texas2020].
+Similarly, Georgia, a Republican stronghold since 1992, voted for the Democratic party, reflecting evolving demographic and ideological shifts [@georgia2020].
+
+Southern states, such as Alabama, Mississippi, and South Carolina with a large amount of Christian population, strongly adhere to conservative principles.
+For example, these states have implemented strict anti-abortion law and advocated for tight immigration policies.
+Furthermore, these states have historically been less supportive of LGBTQ+ rights.
+As a result, voters in these Southern states typically align with the Republican party represented by Trump, which prioritizes pro-life initiatives and traditional Christian values.
 
 ## Third discussion point
+
+maybe talk about employment?
+
+## Talk about mail-in ballots AND Trump's later reaction to losing
 

### 2024-03-11 paper/paper.qmd
changes

@@
 # We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
+political_preferences1 <-
+  readRDS(file = here::here("models/political_preferences1.rds"))
 
@@
 
-# generate predictions for each of our grouped cells
-props$estimate <- predict.glm(political_preferences1, newdata = props,
-                          type = "response")
-
-# create a new column with number of voters from each cell voting Biden
-props <- props %>% mutate(num_voters = n*estimate)
-
-# get errors for our prediction
-errors <- predict.glm(model, newdata = props,
-                      type = "response", se.fit = T)
-lower <- errors$fit - errors$se.fit
-upper <- errors$fit + errors$se.fit
-
-# combine the proportions and the errors we generated
-props_error <- cbind(props, lower, upper)
-props_error <- props_error %>% 
-  rename("lower" = ...11,
-         "upper" = ...12)
-
-# create a new column with number of voters from each cell voting Biden
-props_error <- props_error %>% mutate(num_voters_lower = n*lower,
-                                num_voters_upper = n*upper)
-
-# create a new dataset which contains upper and lower estimates for proportions
-# of votes for each state
-voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
-                                       biden_predict_prop_lower = lower*prop,
-                                       biden_predict_prop_upper = upper*prop) %>%
-  group_by(stateicp) %>%
-  summarise(biden_predict = sum(biden_predict_prop),
-            biden_predict_lower = sum(biden_predict_prop_lower),
-            biden_predict_upper = sum(biden_predict_prop_upper))
+# # generate predictions for each of our grouped cells
+# props$estimate <- predict.glm(political_preferences1, newdata = props,
+#                           type = "response")
+# 
+# # create a new column with number of voters from each cell voting Biden
+# props <- props %>% mutate(num_voters = n*estimate)
+# 
+# # get errors for our prediction
+# errors <- predict.glm(model, newdata = props,
+#                       type = "response", se.fit = T)
+# lower <- errors$fit - errors$se.fit
+# upper <- errors$fit + errors$se.fit
+# 
+# 
+# # combine the proportions and the errors we generated
+# props_error <- cbind(props, lower, upper)
+# props_error <- props_error %>% 
+#   rename("lower" = ...11,
+#          "upper" = ...12)
+# 
+# # create a new column with number of voters from each cell voting Biden
+# props_error <- props_error %>% mutate(num_voters_lower = n*lower,
+#                                 num_voters_upper = n*upper)
+# 
+# # create a new dataset which contains upper and lower estimates for proportions
+# # of votes for each state
+# voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
+#                                        biden_predict_prop_lower = lower*prop,
+#                                        biden_predict_prop_upper = upper*prop) %>%
+#   group_by(stateicp) %>%
+#   summarise(biden_predict = sum(biden_predict_prop),
+#             biden_predict_lower = sum(biden_predict_prop_lower),
+#             biden_predict_upper = sum(biden_predict_prop_upper))
 ```
@@
 ```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
-# get state by state proportions for our polling data
-polling_props <- polling %>% 
-  group_by(stateicp, vote_biden) %>% 
-  summarise(n = n()) %>% 
-  mutate(prop = n/sum(n))
-
-# combine the polling data proportions with the post-stratification data
-poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
-poll_post_biden <- poll_post_biden %>% 
-  filter(vote_biden == 1)
-
-# plot for predictions
-
-poll_post_biden %>% 
-  ggplot(aes(x = employ, y = biden_predict)) +
-  geom_point(aes(color = "black")) +
-  geom_line(aes(group = 1)) +
-  scale_y_continuous(labels = scales::percent) +
-  theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
-  geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
-              alpha = 0.2, fill = "red") +
-  geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
-            linetype = "twodash") +
-  geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
-  geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
-  scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
-  labs(title = "Proportion of People voting for Joe Biden by State",
-       x = "State", y = "Percentage Voting Biden")
+# # get state by state proportions for our polling data
+# polling_props <- polling %>% 
+#   group_by(stateicp, vote_biden) %>% 
+#   summarise(n = n()) %>% 
+#   mutate(prop = n/sum(n)) 
+# 
+# # combine the polling data proportions with the post-stratification data
+# poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
+# poll_post_biden <- poll_post_biden %>% 
+#   filter(vote_biden == 1)
+# 
+# # plot for predictions
+# 
+# poll_post_biden %>% 
+#   ggplot(aes(x = employ, y = biden_predict)) +
+#   geom_point(aes(color = "black")) +
+#   geom_line(aes(group = 1)) +
+#   scale_y_continuous(labels = scales::percent) +
+#   theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
+#   geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
+#               alpha = 0.2, fill = "red") +
+#   geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
+#             linetype = "twodash") +
+#   geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
+#   geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
+#   scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
+#   labs(title = "Proportion of People voting for Joe Biden by State",
+#        x = "State", y = "Percentage Voting Biden")
 ```
@@
 
-# Marginal Effect 
-political_preferences_predictions <- predictions(political_preferences1) |>
-  as_tibble()
-
-political_preferences_predictions
+# # Marginal Effect 
+# political_preferences_predictions <- predictions(political_preferences1) |>
+#   as_tibble()
+# 
+# political_preferences_predictions
 
@@
 ```{r}
-library(margins)
-
-# Marginal effects for each predictor variable
-marginal_effects <- margins(political_preferences1)
-
-# Plotting marginal effects for race
-race_effects <- dyplot(marginal_effects, variables = "race")
-race_effects
-
-# Plotting marginal effects for region
-region_effects <- dyplot(marginal_effects, variables = "region")
-region_effects
-
-# Plotting marginal effects for employ
-employ_effects <- dyplot(marginal_effects, variables = "employ")
-employ_effects
+# library(margins)
+# 
+# # Marginal effects for each predictor variable
+# marginal_effects <- margins(political_preferences1)
+# 
+# # Plotting marginal effects for race
+# race_effects <- dyplot(marginal_effects, variables = "race")
+# race_effects
+# 
+# # Plotting marginal effects for region
+# region_effects <- dyplot(marginal_effects, variables = "region")
+# region_effects
+# 
+# # Plotting marginal effects for employ
+# employ_effects <- dyplot(marginal_effects, variables = "employ")
+# employ_effects
 
@@
 ```{r}
-# Load required libraries
-library(bayestestR)
-
-# Extract posterior draws from the model object
-posterior_draws <- as.matrix(political_preferences1)
-
-# Define the predictor variables for which you want to compute marginal effects
-predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
-                         "Other race", "Two or more races", "White", "Northeast", 
-                         "South", "West", "Homemaker", "Other employment", 
-                         "Part-time", "Permanently disabled", "Retired", 
-                         "Student", "Temporarily laid off", "Unemployed")
-
-# Compute marginal effects
-marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
-
-# Summary of marginal effects
-summary(marginal_effects)
+# # Load required libraries
+# library(bayestestR)
+# 
+# # Extract posterior draws from the model object
+# posterior_draws <- as.matrix(political_preferences1)
+# 
+# # Define the predictor variables for which you want to compute marginal effects
+# predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
+#                          "Other race", "Two or more races", "White", "Northeast", 
+#                          "South", "West", "Homemaker", "Other employment", 
+#                          "Part-time", "Permanently disabled", "Retired", 
+#                          "Student", "Temporarily laid off", "Unemployed")
+# 
+# # Compute marginal effects
+# marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
+# 
+# # Summary of marginal effects
+# summary(marginal_effects)
 
@@
 ```{r}
-library(tidybayes)
-
-# Extract draws from the Bayesian model
-draws <- spread_draws(political_preferences1)
-
-# Plot the posterior distribution of a predictor variable
-ggplot(draws, aes(x = raceBlack)) +
-  geom_density(fill = "skyblue", color = "black") +
-  labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
+# library(tidybayes)
+# 
+# # Extract draws from the Bayesian model
+# draws <- spread_draws(political_preferences1)
+# 
+# # Plot the posterior distribution of a predictor variable
+# ggplot(draws, aes(x = raceBlack)) +
+#   geom_density(fill = "skyblue", color = "black") +
+#   labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
 
@@
 #| message: false
-#| label: fig-modelresults1
-#| fig-cap: "Credible intervals for predictors of support for Biden 1"
+#| label: fig-modelresults2
+#| fig-cap: "Credible intervals for predictors of support for Biden 2"
 # Create the model plot
@@
 
-## Second discussion point
+## Regional Variations
 
@@
 
-## Talk about mail-in ballots AND Trump's later reaction to losing
+## COVID and Mail-in Ballots
+
+Other than race, region, employment, and other usual socioeconomical factors, the special situation of COVID-19 and mail-in-ballots also heavily contributed to the election turnout, leading to Biden's victory.
+Many Republican's shift from Trump to Biden is attributed to Trump's poor COVID responses and policies.
+
+Mail-in-ballots also spanned many controversy over fraud election as Trump claims
 

### 2024-03-11 paper/paper.qmd
ballots

@@
 
-Other than race, region, employment, and other usual socioeconomical factors, the special situation of COVID-19 and mail-in-ballots also heavily contributed to the election turnout, leading to Biden's victory.
-Many Republican's shift from Trump to Biden is attributed to Trump's poor COVID responses and policies.
+In addition to traditional socio-economic factors like race, region, and employment, the unique circumstances surrounding the COVID-19 pandemic and the widespread use of mail-in ballots significantly influenced voter turnout and led to Biden's election victory.
+Trump's handling of the pandemic, including his skepticism towards mask-wearing and disagreements with public health guidance, drew many criticism [@pollitz_long_freed_2020].
+Many dissatisfied Republican voters voted for Biden instead.
 
-Mail-in-ballots also spanned many controversy over fraud election as Trump claims
+Mail-in ballots also played a key role in shaping the election landscape.
+It increased voter participation, particularly among individuals who were reluctant to vote due to logistical constraints or health concerns amid the pandemic.
+Mail-in voting dynamics intensified as the election progressed.
+Initially, Trump led in some states, but as mail-in ballots were counted, the tide often turned in favor of Biden.
+Trump and his supporters raises concerns about fraudulent ballots.
+This controversy cast doubt on the validity of the election process, fueling Trump's claims of a "rigged" election.
 

### 2024-03-11 paper/paper.qmd
added limitations and further studies

@@
 For instance, Texas, a Republican stronghold, saw unprecedented Democratic gains, though ultimately remaining red.
-Notably, the five largest cities in Texas—Houston, San Antonio, Dallas, Austin, and Fort Worth—all backed the Democratic party, marking a significant departure from historical voting patterns [@texas2020].
+Notably, the five largest cities in Texas—Houston, San Antonio, Dallas, Austin, and Fort Worth—all backed the Democratic party [@texas2020].
 Similarly, Georgia, a Republican stronghold since 1992, voted for the Democratic party, reflecting evolving demographic and ideological shifts [@georgia2020].
@@
 In addition to traditional socio-economic factors like race, region, and employment, the unique circumstances surrounding the COVID-19 pandemic and the widespread use of mail-in ballots significantly influenced voter turnout and led to Biden's election victory.
-Trump's handling of the pandemic, including his skepticism towards mask-wearing and disagreements with public health guidance, drew many criticism [@pollitz_long_freed_2020].
+Trump's handling of the pandemic, including his skepticism towards mask-wearing and vaccination and disagreements with public health guidance, drew many criticism [@pollitz_long_freed_2020].
 Many dissatisfied Republican voters voted for Biden instead.
@@
 Mail-in ballots also played a key role in shaping the election landscape.
-It increased voter participation, particularly among individuals who were reluctant to vote due to logistical constraints or health concerns amid the pandemic.
-Mail-in voting dynamics intensified as the election progressed.
+It increased voter participation, particularly among individuals who were reluctant to vote due to logistical constraints or health concerns amid the pandemic [@amlani_collitt_2022].
+Mail-in ballots raised many election controversies.
 Initially, Trump led in some states, but as mail-in ballots were counted, the tide often turned in favor of Biden.
-Trump and his supporters raises concerns about fraudulent ballots.
-This controversy cast doubt on the validity of the election process, fueling Trump's claims of a "rigged" election.
+Trump and his supporters raises concerns about the legitimacy of the  ballots and claimed the election is "rigged" [@axelrod_2022].
+However, there is no solid proof that the election is "rigged."
 
@@
 
-add more weakness about the data, graphs, etc.
-
 One weakness of using a logistic regression model is its inability to predict voting turnout for candidates beyond the Biden or Trump.
 Expanding the analysis to include other candidates would enhance its comprehensiveness.
-Furthermore, the reliability of our findings is contingent upon the accuracy of the survey data.
+Furthermore, the reliability of our findings is based on the accuracy of the survey data.
 Respondents may provide inaccurate or misleading information, intentionally or unintentionally, leading to biased estimates and unreliable predictions.
+Due to many controversial opinions and actions of Trump and his supporters, many Republican who voted for him might be reluctant to admit their voting in the survey.
 Additionally, missing data (N/As) can introduce further challenges, as logistic regression requires complete data for accurate modeling.
 
+Furthermore, it's important to recognize that our findings establish correlation, not causation.
+Because we only controlled few variables for election turnout, our results may lack essential variables and thus suffer from omitted variable bias.
+Critical factors such as the impact of mail-in ballots, the role of social media, and broader socio-political dynamics that may have impacted the election are not incorporated in the model.
+
+For further studies, we could start by incorporating more socio-economicalindicators such as income levels, education, and urbanization rate that attribute to the election turnout.
+Analyzing sentiment from social media platforms, news articles, and public forums could offer a real-time perspective on voter attitudes leading up to the election.
+We could also add in state dummies to observe for election turnouts by state.
+To infer causality, future research should employ advanced methodologies capable of addressing issues like selection bias and heterogeneity treatment bias.
 \newpage

### 2024-03-11 paper/paper.qmd
add data section, add r package to bib

--- 2024-03-11 paper/paper.qmd
@@
 library(tidyverse)
-library(palmerpenguins)
 library(here)
@@
 library(margins)
-
+library(kableExtra)
 ```
@@
 This report consists of four sections, not including the introduction.
-In Section 2, we look at the data used for our report and include some tables and graphs to illustrate the different groups of people in our data.
-In section 3, we build the model and discuss its justification and explanation.
-The results of our predictions is highlighted in the Section 4 using tables and graphs.
+In @sec-data, we look at the data used for our report and include some tables and graphs to illustrate the different groups of people in our data.
+In @sec-model, we build the model and discuss its justification and explanation.
+The results of our predictions is highlighted in @sec-result using tables and graphs.
 Lastly, discussions are conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.
-
-In this report, R statistical programming language is used, with R packages: [a lot of citations needed]
 
@@
 
+## Data Source
+In this report, we use the 2020 Cooperative Election Study (CES) (@citeCes2020) as out primary dataset.
+This is a long-established annual political survey of US.
+CES contains information about how Americans view Congress and hold their representatives accountable in elections, how they vote and their electoral experiences, and how their behaviors and experiences vary with political geography and social context.
+In 2020, there were 61,000 American adults completed the survey.
+
 ## Data Measurement
 
-## Summary Statistics
+## Features
+The original CES 2020 dataset, which shows in @tbl-raw, contains 61000 observations and 5 variables, which are "votereg", "CC20_410", "race", "region", "employ".
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+1. votereg: whether the respondent is registered to vote.
+
+2. CC20_410: the person that respondent vote for President of the United States.
+
+3. race: the census region where the respondent lives.
+
+4. region: the racial or ethnic group of the respondent.
+
+5. employ: the current employment status of the respondent.
 
 ```{r}
-# read in data
+#| include: false
+#| warning: false
+#| message: false
+
+# read in raw data
+raw_ces2020 <-  read_csv(here::here("data/raw_data/ces2020.csv"))
+```
+
+```{r}
+#| label: tbl-raw
+#| tbl-cap: "Preview of the raw 2020 US Cooperative Election Study (CES) dataset"
+#| message: false
+#| echo: false
+
+raw_ces2020[1:5, 1:5] |>
+  kable()
+```
+
+## Methodology
+Since it is difficult to observe through 61000 rows with 5 variables, this report will only explore and analyze through specific aspects.
+The original dataset contains respondent's voter registration status and the person that respondent vote for President of the United States.
+This paper will only analyze respondents who are registered to vote and focus on only two voting options, Biden and Trump.
+
+The dataset is cleaned by rename the column names, specify the class of the columns, and change the numbers in the table to the corresponding description in the codebook to improve the readability.
+In addition, the cleaned data removes NA employment status since there are only 34 rows, which is a small amount of missing value compared with 61000 rows.
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), and `kableExtra` (@citeKableExtra).
+@tbl-clean-data shows a preview of the cleaned dataset.
+@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset.
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+# read in cleaned data
 ces2020 <-  read_csv(here::here("data/analysis_data/cleaned_ces2020.csv"))
@@
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
+
 # change column type to factor
@@
 
-# Model
+```{r}
+#| label: tbl-clean-data
+#| tbl-cap: "Preview of the cleaned 2020 CES dataset"
+#| message: false
+#| echo: false
+
+ces2020[1:5, 1:4] |>
+  kable()
+```
+
+```{r}
+#| label: tbl-summary
+#| tbl-cap: "Statistics summary of the cleaned 2020 CES dataset"
+#| message: false
+#| echo: false
+
+ces2020 |>
+  summary()
+```
+
+# Model {#sec-model}
 
@@
 # We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
-political_preferences1 <-
-  readRDS(file = here::here("models/political_preferences1.rds"))
 
@@
 
-# Results
+# Results {#sec-result}
 
@@
 
-# # generate predictions for each of our grouped cells
-# props$estimate <- predict.glm(political_preferences1, newdata = props,
-#                           type = "response")
-# 
-# # create a new column with number of voters from each cell voting Biden
-# props <- props %>% mutate(num_voters = n*estimate)
-# 
-# # get errors for our prediction
-# errors <- predict.glm(model, newdata = props,
-#                       type = "response", se.fit = T)
-# lower <- errors$fit - errors$se.fit
-# upper <- errors$fit + errors$se.fit
-# 
-# 
-# # combine the proportions and the errors we generated
-# props_error <- cbind(props, lower, upper)
-# props_error <- props_error %>% 
-#   rename("lower" = ...11,
-#          "upper" = ...12)
-# 
-# # create a new column with number of voters from each cell voting Biden
-# props_error <- props_error %>% mutate(num_voters_lower = n*lower,
-#                                 num_voters_upper = n*upper)
-# 
-# # create a new dataset which contains upper and lower estimates for proportions
-# # of votes for each state
-# voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
-#                                        biden_predict_prop_lower = lower*prop,
-#                                        biden_predict_prop_upper = upper*prop) %>%
-#   group_by(stateicp) %>%
-#   summarise(biden_predict = sum(biden_predict_prop),
-#             biden_predict_lower = sum(biden_predict_prop_lower),
-#             biden_predict_upper = sum(biden_predict_prop_upper))
+# generate predictions for each of our grouped cells
+props$estimate <- predict.glm(political_preferences1, newdata = props,
+                          type = "response")
+
+# create a new column with number of voters from each cell voting Biden
+props <- props %>% mutate(num_voters = n*estimate)
+
+# get errors for our prediction
+errors <- predict.glm(model, newdata = props,
+                      type = "response", se.fit = T)
+lower <- errors$fit - errors$se.fit
+upper <- errors$fit + errors$se.fit
+
+# combine the proportions and the errors we generated
+props_error <- cbind(props, lower, upper)
+props_error <- props_error %>% 
+  rename("lower" = ...11,
+         "upper" = ...12)
+
+# create a new column with number of voters from each cell voting Biden
+props_error <- props_error %>% mutate(num_voters_lower = n*lower,
+                                num_voters_upper = n*upper)
+
+# create a new dataset which contains upper and lower estimates for proportions
+# of votes for each state
+voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
+                                       biden_predict_prop_lower = lower*prop,
+                                       biden_predict_prop_upper = upper*prop) %>%
+  group_by(stateicp) %>%
+  summarise(biden_predict = sum(biden_predict_prop),
+            biden_predict_lower = sum(biden_predict_prop_lower),
+            biden_predict_upper = sum(biden_predict_prop_upper))
 ```
@@
 ```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
-# # get state by state proportions for our polling data
-# polling_props <- polling %>% 
-#   group_by(stateicp, vote_biden) %>% 
-#   summarise(n = n()) %>% 
-#   mutate(prop = n/sum(n)) 
-# 
-# # combine the polling data proportions with the post-stratification data
-# poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
-# poll_post_biden <- poll_post_biden %>% 
-#   filter(vote_biden == 1)
-# 
-# # plot for predictions
-# 
-# poll_post_biden %>% 
-#   ggplot(aes(x = employ, y = biden_predict)) +
-#   geom_point(aes(color = "black")) +
-#   geom_line(aes(group = 1)) +
-#   scale_y_continuous(labels = scales::percent) +
-#   theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
-#   geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
-#               alpha = 0.2, fill = "red") +
-#   geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
-#             linetype = "twodash") +
-#   geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
-#   geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
-#   scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
-#   labs(title = "Proportion of People voting for Joe Biden by State",
-#        x = "State", y = "Percentage Voting Biden")
+# get state by state proportions for our polling data
+polling_props <- polling %>% 
+  group_by(stateicp, vote_biden) %>% 
+  summarise(n = n()) %>% 
+  mutate(prop = n/sum(n))
+
+# combine the polling data proportions with the post-stratification data
+poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
+poll_post_biden <- poll_post_biden %>% 
+  filter(vote_biden == 1)
+
+# plot for predictions
+
+poll_post_biden %>% 
+  ggplot(aes(x = employ, y = biden_predict)) +
+  geom_point(aes(color = "black")) +
+  geom_line(aes(group = 1)) +
+  scale_y_continuous(labels = scales::percent) +
+  theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
+  geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
+              alpha = 0.2, fill = "red") +
+  geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
+            linetype = "twodash") +
+  geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
+  geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
+  scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
+  labs(title = "Proportion of People voting for Joe Biden by State",
+       x = "State", y = "Percentage Voting Biden")
 ```
@@
 
-# # Marginal Effect 
-# political_preferences_predictions <- predictions(political_preferences1) |>
-#   as_tibble()
-# 
-# political_preferences_predictions
+# Marginal Effect 
+political_preferences_predictions <- predictions(political_preferences1) |>
+  as_tibble()
+
+political_preferences_predictions
 
@@
 ```{r}
-# library(margins)
-# 
-# # Marginal effects for each predictor variable
-# marginal_effects <- margins(political_preferences1)
-# 
-# # Plotting marginal effects for race
-# race_effects <- dyplot(marginal_effects, variables = "race")
-# race_effects
-# 
-# # Plotting marginal effects for region
-# region_effects <- dyplot(marginal_effects, variables = "region")
-# region_effects
-# 
-# # Plotting marginal effects for employ
-# employ_effects <- dyplot(marginal_effects, variables = "employ")
-# employ_effects
+library(margins)
+
+# Marginal effects for each predictor variable
+marginal_effects <- margins(political_preferences1)
+
+# Plotting marginal effects for race
+race_effects <- dyplot(marginal_effects, variables = "race")
+race_effects
+
+# Plotting marginal effects for region
+region_effects <- dyplot(marginal_effects, variables = "region")
+region_effects
+
+# Plotting marginal effects for employ
+employ_effects <- dyplot(marginal_effects, variables = "employ")
+employ_effects
 
@@
 ```{r}
-# # Load required libraries
-# library(bayestestR)
-# 
-# # Extract posterior draws from the model object
-# posterior_draws <- as.matrix(political_preferences1)
-# 
-# # Define the predictor variables for which you want to compute marginal effects
-# predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
-#                          "Other race", "Two or more races", "White", "Northeast", 
-#                          "South", "West", "Homemaker", "Other employment", 
-#                          "Part-time", "Permanently disabled", "Retired", 
-#                          "Student", "Temporarily laid off", "Unemployed")
-# 
-# # Compute marginal effects
-# marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
-# 
-# # Summary of marginal effects
-# summary(marginal_effects)
+# Load required libraries
+library(bayestestR)
+
+# Extract posterior draws from the model object
+posterior_draws <- as.matrix(political_preferences1)
+
+# Define the predictor variables for which you want to compute marginal effects
+predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
+                         "Other race", "Two or more races", "White", "Northeast", 
+                         "South", "West", "Homemaker", "Other employment", 
+                         "Part-time", "Permanently disabled", "Retired", 
+                         "Student", "Temporarily laid off", "Unemployed")
+
+# Compute marginal effects
+marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
+
+# Summary of marginal effects
+summary(marginal_effects)
 
@@
 ```{r}
-# library(tidybayes)
-# 
-# # Extract draws from the Bayesian model
-# draws <- spread_draws(political_preferences1)
-# 
-# # Plot the posterior distribution of a predictor variable
-# ggplot(draws, aes(x = raceBlack)) +
-#   geom_density(fill = "skyblue", color = "black") +
-#   labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
+library(tidybayes)
+
+# Extract draws from the Bayesian model
+draws <- spread_draws(political_preferences1)
+
+# Plot the posterior distribution of a predictor variable
+ggplot(draws, aes(x = raceBlack)) +
+  geom_density(fill = "skyblue", color = "black") +
+  labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
 
@@
 #| label: fig-modelresults2
-#| fig-cap: "Credible intervals for predictors of support for Biden 2"
+#| fig-cap: "Credible intervals for predictors of support for Biden 1"
 # Create the model plot
@@
 
-## Regional Variations
+## Second discussion point
 
@@
 
-## COVID and Mail-in Ballots
-
-Other than race, region, employment, and other usual socioeconomical factors, the special situation of COVID-19 and mail-in-ballots also heavily contributed to the election turnout, leading to Biden's victory.
-Many Republican's shift from Trump to Biden is attributed to Trump's poor COVID responses and policies.
-
-Mail-in-ballots also spanned many controversy over fraud election as Trump claims
+## Talk about mail-in ballots AND Trump's later reaction to losing
 

### 2024-03-12 paper/paper.qmd

--- 2024-03-11 paper/paper.qmd
@@
 
-This report consists of four sections, not including the introduction.
-In Section 2, we look at the data used for our report and include some tables and graphs to illustrate the different groups of people in our data.
-In section 3, we build the model and discuss its justification and explanation.
-The results of our predictions is highlighted in the Section 4 using tables and graphs.
-Lastly, discussions are conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.
-
-In this report, R statistical programming language is used, with R packages: [a lot of citations needed]
+The remainder of this paper is structured into different sections.
+@sec-data demonstrates the data used for our report and includes some tables and graphs to illustrate the different groups of people in our data.
+@sec-model builds the model and discusses its justification and explanation.
+@sec-result highlights the results of the predictions using tables and graphs.
+@sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.
 
@@
   labs(x = "90% Credibility Interval")
-
 ```
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-03-12 paper/us_election_2020.qmd
update paper.qmd

--- 2024-03-12 paper/paper.qmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election"
 author: 
-  - First author
-  - Another author
+  - Hannah Yu
+  - Mary Cheng
+  - Yimiao Yuan
 thanks: "Code and data are available at: https://github.com/hannahyu07/US-Election"
@@
 ## Estimand
+real vote_for biden or trump
 
@@
 In addition, the cleaned data removes NA employment status since there are only 34 rows, which is a small amount of missing value compared with 61000 rows.
+After []
+
 The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), and `kableExtra` (@citeKableExtra).
 @tbl-clean-data shows a preview of the cleaned dataset.
-@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset.
 
@@
 
+@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset. ***add detail***
 ```{r}
@@
 ces2020 |>
-  summary()
+  summary() |>
+  kable()
 ```
@@
 # Model {#sec-model}
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in
-
-[Appendix -@sec-model-details].
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm.
+We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm.
 We use the default priors from `rstanarm`.
 Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters.
-To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix A).
+To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
+Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see -@sec-model-details).
 
@@
 ## Data Result
+
+```{r}
+
+ces2020 |>
+  ggplot(aes(x = race, fill = voted_for)) +
+  geom_bar() +
+  coord_flip()
+```
+
 @fig-race_region shows the relationship between race, region, and voting preference.
@@
 #| echo: false
+#| warning: false
+#| message: false
 
@@
 ```
+
 @fig-race_employ illustrates the relationship between region, employment status, and voting preferences for Trump and Biden.
@@
 ```{r}
-# #| label: fig-race_employ_white
-# #| fig-cap: The distribution of presidential preferences, by region and employment status, only white people
-# #| echo: false
-# 
-# ces2020_selected_data <- ces2020[ces2020$race == "White", ]
-# 
-# ces2020_selected_data |>
-#   ggplot(aes(x = employ, fill = voted_for)) +
-#   stat_count(position = "dodge") +
-#   facet_wrap(facets = vars(region)) +
-#   theme_minimal() +
-#   labs(
-#     x = "Employment status",
-#     y = "Number of respondents",
-#     fill = "Voted for"
-#   ) +
-#   coord_flip() +
-#   scale_fill_brewer(palette = "Set1") +
-#   theme(legend.position = "bottom")
+#| label: fig-race_employ_region
+#| fig-cap: "The distribution of presidential preferences, by race, region and employment status"
+#| echo: false
+#| warning: false
+#| message: false
+#| include: false
+
+# plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("red", "blue")) %>% 
+#   add_markers(color = ces2020$voted_for, opacity = 0.03, size = 0.4) %>%
+#   layout(xaxis = list(title = 'Race'), yaxis = list(title = 'Region'), zaxis = list(title = 'Employment Status')) %>%
+#   layout(xaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
+#          yaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
+#          zaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)))
 ```
-
-This bubble plot illustrates four variables: race, region, employment status, and voting preference.
+This bubble plot (@fig-race_employ_region) illustrates four variables: race, region, employment status, and voting preference.
 Darker dots indicate a higher number of people, with red representing Trump supporters and blue for Biden supporters.
@@
 In those purple dots, we found that mostly are from people who are either Native American or from the South.
-```{r}
-#| label: fig-race_employ_region
-#| fig-cap: The distribution of presidential preferences, by race, region and employment status
-#| echo: false
-
-plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("red", "blue")) %>% 
-  add_markers(color = ces2020$voted_for, opacity = 0.03, size = 0.4) %>%
-  layout(xaxis = list(title = 'Race'), yaxis = list(title = 'Region'), zaxis = list(title = 'Employment Status')) %>%
-  layout(xaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
-         yaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
-         zaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)))
-```
 
@@
 
-```{r prediction, echo=F, warning=F, message=F}
-
-# # generate predictions for each of our grouped cells
-# props$estimate <- predict.glm(political_preferences1, newdata = props,
-#                           type = "response")
-# 
-# # create a new column with number of voters from each cell voting Biden
-# props <- props %>% mutate(num_voters = n*estimate)
-# 
-# # get errors for our prediction
-# errors <- predict.glm(model, newdata = props,
-#                       type = "response", se.fit = T)
-# lower <- errors$fit - errors$se.fit
-# upper <- errors$fit + errors$se.fit
-# 
-# 
-# # combine the proportions and the errors we generated
-# props_error <- cbind(props, lower, upper)
-# props_error <- props_error %>% 
-#   rename("lower" = ...11,
-#          "upper" = ...12)
-# 
-# # create a new column with number of voters from each cell voting Biden
-# props_error <- props_error %>% mutate(num_voters_lower = n*lower,
-#                                 num_voters_upper = n*upper)
-# 
-# # create a new dataset which contains upper and lower estimates for proportions
-# # of votes for each state
-# voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
-#                                        biden_predict_prop_lower = lower*prop,
-#                                        biden_predict_prop_upper = upper*prop) %>%
-#   group_by(stateicp) %>%
-#   summarise(biden_predict = sum(biden_predict_prop),
-#             biden_predict_lower = sum(biden_predict_prop_lower),
-#             biden_predict_upper = sum(biden_predict_prop_upper))
-```
-
-```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
-# # get state by state proportions for our polling data
-# polling_props <- polling %>% 
-#   group_by(stateicp, vote_biden) %>% 
-#   summarise(n = n()) %>% 
-#   mutate(prop = n/sum(n)) 
-# 
-# # combine the polling data proportions with the post-stratification data
-# poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
-# poll_post_biden <- poll_post_biden %>% 
-#   filter(vote_biden == 1)
-# 
-# # plot for predictions
-# 
-# poll_post_biden %>% 
-#   ggplot(aes(x = employ, y = biden_predict)) +
-#   geom_point(aes(color = "black")) +
-#   geom_line(aes(group = 1)) +
-#   scale_y_continuous(labels = scales::percent) +
-#   theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
-#   geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
-#               alpha = 0.2, fill = "red") +
-#   geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
-#             linetype = "twodash") +
-#   geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
-#   geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
-#   scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
-#   labs(title = "Proportion of People voting for Joe Biden by State",
-#        x = "State", y = "Percentage Voting Biden")
-```
-
 Our results are summarized in @tbl-modelresults.
-
-```{r}
-
-# # Marginal Effect 
-# political_preferences_predictions <- predictions(political_preferences1) |>
-#   as_tibble()
-# 
-# political_preferences_predictions
-
-```
-
-```{r}
-# library(margins)
-# 
-# # Marginal effects for each predictor variable
-# marginal_effects <- margins(political_preferences1)
-# 
-# # Plotting marginal effects for race
-# race_effects <- dyplot(marginal_effects, variables = "race")
-# race_effects
-# 
-# # Plotting marginal effects for region
-# region_effects <- dyplot(marginal_effects, variables = "region")
-# region_effects
-# 
-# # Plotting marginal effects for employ
-# employ_effects <- dyplot(marginal_effects, variables = "employ")
-# employ_effects
-
-```
 
@@
 ```{r}
-# # Load required libraries
-# library(bayestestR)
-# 
-# # Extract posterior draws from the model object
-# posterior_draws <- as.matrix(political_preferences1)
-# 
-# # Define the predictor variables for which you want to compute marginal effects
-# predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
-#                          "Other race", "Two or more races", "White", "Northeast", 
-#                          "South", "West", "Homemaker", "Other employment", 
-#                          "Part-time", "Permanently disabled", "Retired", 
-#                          "Student", "Temporarily laid off", "Unemployed")
-# 
-# # Compute marginal effects
-# marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
-# 
-# # Summary of marginal effects
-# summary(marginal_effects)
-
-```
-
-```{r}
-# library(tidybayes)
-# 
-# # Extract draws from the Bayesian model
-# draws <- spread_draws(political_preferences1)
-# 
-# # Plot the posterior distribution of a predictor variable
-# ggplot(draws, aes(x = raceBlack)) +
-#   geom_density(fill = "skyblue", color = "black") +
-#   labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")
-
-```
-
-```{r}
+#| include: false
 # Extract posterior samples
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
+race
+white
+- religion
 
-maybe talk about race?
+Biden: white, asian(trump covid), black, hispanic(trump建墙, no illegal immigration), other
+Trump: white, two or more races, 
+```{r}
+ces2020|>
+  filter(voted_for == "Biden") |>
+  select(race) |>
+  summary()
+```
+```{r}
+ces2020|>
+  filter(voted_for == "Trump") |>
+  select(race) |>
+  summary()
+```
 
@@
 Trump and his supporters raises concerns about the legitimacy of the  ballots and claimed the election is "rigged" [@axelrod_2022].
-However, there is no solid proof that the election is "rigged."
+However, there is no solid proof that the election is "rigged".
 
@@
 
-For further studies, we could start by incorporating more socio-economicalindicators such as income levels, education, and urbanization rate that attribute to the election turnout.
+For further studies, we could start by incorporating more socio-economical indicators such as income levels, education, and urbanization rate that attribute to the election turnout.
 Analyzing sentiment from social media platforms, news articles, and public forums could offer a real-time perspective on voter attitudes leading up to the election.
@@
 To infer causality, future research should employ advanced methodologies capable of addressing issues like selection bias and heterogeneity treatment bias.
+
 \newpage
@@
 
-# plot(first_model, "trace")
-# 
-# plot(first_model, "rhat")
+ plot(political_preferences1, "trace")
+
+ plot(political_preferences1, "rhat")
 ```

### 2024-03-12 scripts/04-model.R
fixed model

@@ -6,7 +6,6 @@
 # License: MIT
 # Pre-requisites: run 01-download_data.R and 02-data_cleaning.R first to 
 # get the cleaned dataset
-# Any other information needed?
 
 
 #### Workspace setup ####
@@ -46,76 +45,4 @@ saveRDS(
   political_preferences1,
   file = "models/political_preferences1.rds"
 )
-
-
-# Model 2 for South
-# Filter data to include only observations where region is "South"
-ces2020_reduced_south <- subset(analysis_data, region == "South")
-
-# Sample 1000 observations from the filtered dataset
-ces2020_reduced_south <- ces2020_reduced_south[sample(nrow(ces2020_reduced_south), 1000), ]
-
-# Fit logistic regression model using the filtered dataset
-political_preferences2 <- stan_glm(
-  voted_for_binary ~ race + employ,
-  data = ces2020_reduced_south,
-  family = binomial(link = "logit"),
-  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  seed = 123
-)
-#### Save model ####
-saveRDS(
-  political_preferences2,
-  file = "models/political_preferences2.rds"
-)
-
-# Model 3 for Northeast
-
-# Filter data to include only observations where region is "Northeast"
-ces2020_reduced_north <- subset(analysis_data, region == "Northeast")
-
-# Sample 1000 observations from the filtered dataset
-ces2020_reduced_north <- ces2020_reduced_north[sample(nrow(ces2020_reduced_north), 1000), ]
-
-# Fit logistic regression model using the filtered dataset
-political_preferences3 <- stan_glm(
-  voted_for_binary ~ race + employ,
-  data = ces2020_reduced_north,
-  family = binomial(link = "logit"),
-  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  seed = 123
-)
-#### Save model ####
-saveRDS(
-  political_preferences3,
-  file = "models/political_preferences3.rds"
-)
-
-
-# Model 4 for West
-# Filter data to include only observations where region is "West"
-ces2020_reduced_west <- subset(analysis_data, region == "West")
-
-# Sample 1000 observations from the filtered dataset
[…]

### 2024-03-12 paper/us_election_2020.qmd
more changes in methodology

@@
 
+The transformation of real-world phenomena into quantifiable data points in our dataset is influenced by various factors, leading to inherent limitations in our measurements for our variables: "votereg", ", and political affiliation.
+
 ## Features
-The original CES 2020 dataset, which shows in @tbl-raw, contains 61000 observations and 5 variables, which are "votereg", "CC20_410", "race", "region", "employ".
+The original CES 2020 dataset, which shows in @tbl-raw, contains 61000 observations and many variables.
+We chose to feature these 5 variables: "votereg", "CC20_410", "race", "region", "employ", in our analysis.
 
@@
 
-2. CC20_410: the person that respondent vote for President of the United States.
+2. CC20_410: the presidential candidate the respondent voted for.
 
@@
 ## Methodology
-Since it is difficult to observe through 61000 rows with 5 variables, this report will only explore and analyze through specific aspects.
-The original dataset contains respondent's voter registration status and the person that respondent vote for President of the United States.
-This paper will only analyze respondents who are registered to vote and focus on only two voting options, Biden and Trump.
+Since it is difficult to observe such as large dataset, this report will only explore and analyze through specific aspects.
+The original dataset contains respondent's voter registration status and the presidential candidate the respondent voted for.
+This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden representing the Democratic party and Donald Trump representing the Republican party.
 

### 2024-03-12 paper/us_election_2020.qmd
update data section

@@
 In addition, the cleaned data removes NA employment status since there are only 34 rows, which is a small amount of missing value compared with 61000 rows.
-After []
+After cleaning, 43534 rows of data and 4 variables remain.
 
@@
 
-@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset. ***add detail***
+@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset.
+As we can see from the table, there are more people who support Biden.
+Respondents covered a wide range of races, with white people being the most heavily represented.
+Also, CES data came from a variety of locations, but the majority came from the southern region of the United States.
+The employment status of those who completed the survey varied, with most of them being full-time or retired.
 ```{r}
@@
 Biden: white, asian(trump covid), black, hispanic(trump建墙, no illegal immigration), other
-Trump: white, two or more races, 
-```{r}
-ces2020|>
-  filter(voted_for == "Biden") |>
-  select(race) |>
-  summary()
-```
-```{r}
-ces2020|>
-  filter(voted_for == "Trump") |>
-  select(race) |>
-  summary()
-```
+Trump: white, two or more races, Middle Eastern
 

### 2024-03-12 paper/us_election_2020.qmd
data measurement

--- 2024-03-12 paper/us_election_2020.qmd
@@
 
-## Data Measurement
-
-The transformation of real-world phenomena into quantifiable data points in our dataset is influenced by various factors, leading to inherent limitations in our measurements for our variables: "votereg", ", and political affiliation.
-
 ## Features
@@
 ```
+## Data Measurement
+
+Our dataset's quantitative representation of real-world phenomena is influenced by several factors, which inherently limit the accuracy of our measurements for the five variables.
+
+Firstly, for the variable "votereg" indicating whether a respondent is registered to vote, the measurement process involves relying on self-reported information from survey respondents.
+The US voter registration system is known to be inaccurate and inefficient.While efforts are made to ensure accuracy, there may be instances of misreporting or misunderstanding of voter registration status, leading to potential inaccuracies in the data.
+According to [@inaccurate], there are millions of voter registrations that are no longer valid or inaccurate.
+There may also be cases when individuals falsely believed they are registered to vote because they reached the voting age but did not actually register at their local office.
+
+Regarding "CC20_410," representing the presidential candidate the respondent voted for, data collection relies on self-reporting, which is subject to recall bias and social desirability bias.
+While the data collection occurred before the notorious January 6, 2021 United States Capitol Attack that resulted in international criticism and increased the unpopularity of Trump in mainstream media, Trump had made many speeches and taken actions throughout his presidency that contributed to his polarizing image.
+Among many voters, voting for Trump became associated with characteristics such as being uneducated, backward-thinking, and anti-science.
+As a result, individuals who voted for him may have felt social pressure to conceal or lie about their support, potentially leading to underreporting of votes for Trump in the survey data.
+
+For the variable "race," which denotes the racial or ethnic group of the respondent, categorization relies on self-identification.
+However, racial identity is complex and can be influenced by cultural, social, and historical factors.
+Mixed-race individuals, for instance, may choose to identify with one racial group over another based on social preferences or personal experiences.
+Moreover, the race variable includes a category for "two or more races" to classify individuals identifying with multiple racial backgrounds.
+While this acknowledges the diversity within the population, it may not capture the nuances of each individual's identity.
+Additionally, the absence of a distinct category for "Indians or South Asians" presents a limitation.
+While these individuals may technically fall under the category "Asian," many Indian and South Asian Americans may prefer to identify separately due to differences in appearance and cultural background.
+The term "Asians" are more generally associated with East Asians such as Chinese, Japanese, and Koreans.
+As a result, there's a potential for misclassification, with some individuals opting to report themselves as belonging to the "other" race category instead.
+
+In the case of "region," which represents the census region where the respondent lives, data collection relies on categorization based on geographical location.
+However, it's important to note that regional boundaries can sometimes be arbitrary and may not fully capture the diverse cultural, economic, and social affiliations of individuals.
+Additionally, people living in bordering states or areas near regional boundaries may have affiliations with multiple regions or may identify more strongly with a neighboring region.
+For example, states like Missouri and Kentucky are often considered part of the Midwest, but they also share cultural and economic ties with the South.
+This complexity can lead to challenges in accurately categorizing individuals based on their region of residence, potentially resulting in oversimplification or misrepresentation of regional identities and characteristics.
+
+The "region" variable categorizes respondents based on their geographical location into four census regions: Northeast, Midwest, South, and West.
+However, regional boundaries can be arbitrary, and individuals living in bordering areas may have affiliations with multiple regions or identify more strongly with a neighboring region.
+For instance, states like Missouri and Kentucky are often considered part of the Midwest but also share cultural and economic ties with the South.
+This complexity can make individuals accurately reporting thier region challenging.
+
+Finally, for "employ", indicating the respondent's self-reporting employment status, can be influenced by various factors such as job changes, seasonal work, and personal circumstances.
+In addition, individuals may intentionally misreport their employment status due to societal pressures or to access benefits.
+For instance, some may falsely claim employment to avoid stigma, while others may report unemployment to qualify for unemployment benefits.
+Additionally, students working part-time jobs may selectively report their status based on their perceived benefit.
+These discrepancies can introduce bias and inaccuracies into the data, impacting the reliability of our analyses.
 

### 2024-03-12 paper/us_election_2020.qmd
complete intro

@@
 Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
-His winning was surprising and it led people to challenge the preconceived notions and reliability of pre-election polling data [citation needed].
-On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign [citation needed].
+On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign.
 He aimed to regain control from the Republican party.
-In the end, Biden won the election by 51.3% majority votes [citation needed].
-It is important for us to understand how various demographic, economic, and social factors may influence individuals' voting decisions, which is why we decide to analyze the 2020 election data set and build a prediction model.
-This allows us to discover trends and address potential issues in society to better reflect the needs and preferences of diverse communities.
+In the end, Biden won the election by 51.3% majority votes (@cnn_2020), which Trump questioned its credibility.
+Due to the COVID-19 pandemic in 2020, the vote system changed to in-mail voting instead of in-person voting, which was why Trump believed that some votes were stolen (@trump_stolenvote).
+Therefore, it is important for us to analyze why people voted for Biden and Trump in 2020 election and how various demographic, economic, and social factors may influence individuals' voting decisions.
+Perhaps then we could see why Biden eventually won.
+We analyze the 2020 election data set from Cooperative Election Study (CES) [citation needed] and build a prediction model for individual voting preference.
+This allows us to discover trends and address potential political, economic, and societal issues to better reflect the needs and preferences of diverse communities.
 
-In this paper, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study (CES)  [citation needed].
+In this paper, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study.
 Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
 Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set, which are race, region that they live, and employment status.
+The estimand in this paper is the number of people who support Trump and Biden in reality.
+However, it is difficult to measure the exact number of people who support Trump and Biden since there are millions of people in the United States and not all of them with the rights to vote would actually vote.
+Therefore, in this paper, we attempt to estimate the estimand using a logistic regression model which is trained using 2020 election data set from CES.
 
-**add： 4) what was done; 5) what was found after we finish the results section
+We found that in the 2020 presidential election, Biden had strong support from racial groups including black, Hispanic, and Asian populations.
+Geographically, Biden gained greater support in the Northeast and West regions, while Trump secured more votes in the South.
+Additionally, both full-time and part-time workers, as well as students and those facing unemployment or layoffs, leaned towards Biden.
 
@@
 @sec-result highlights the results of the predictions using tables and graphs.
-@sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.
-
-## Estimand
-real vote_for biden or trump
+@sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, employment status, and the influence of COVID-19 and in-mail voting systems.
 

### 2024-03-12 scripts/05-test_class.R
update model tests

@@ -1,0 +1,18 @@
+#### Preamble ####
+# Purpose: Tests the model class
+# Author: Hannah Yu
+# Date: 06 March 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# Pre-requisites: run 04-model.R to get model
+
+library("testthat")
+
+test_that("Check class", {
+  # Check if the model object inherits from any of the expected classes
+  expect_true(
+    inherits(political_preferences1, "stanreg") ||
+      inherits(political_preferences1, "glm") ||
+      inherits(political_preferences1, "lm"),
+    info = "The class of political_preferences1 is as expected."
+  )
+})

### 2024-03-12 scripts/06-test_observations.R

@@ -1,0 +1,13 @@
+#### Preamble ####
+# Purpose: Tests the model number of observations
+# Author: Hannah Yu
+# Date: 06 March 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# Pre-requisites: run 04-model.R to get model
+
+test_that("Check number of observations is correct", {
+  # Check if the number of observations is equal to 1000
+  expect_equal(nrow(political_preferences1$data), 1000,
+               info = "The number of observations is 1000."
+  )
+})

### 2024-03-12 scripts/07-test_coefficients.R

@@ -1,0 +1,12 @@
+#### Preamble ####
+# Purpose: Tests the model cofficient
+# Author: Hannah Yu
+# Date: 06 March 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# Pre-requisites: run 04-model.R to get model
+
+
+test_that("Check summary", {
+  summary_political <- summary(political_preferences1)
+  expect_true("summary.stanreg" %in% class(summary_political))
+})

### 2024-03-12 paper/us_election_2020.qmd
added graph in result section

@@
 
+@fig-race shows the relationship between race and voting preference.
+Overall, Biden gets more support from most racial groups, except for Native Americans and people of "two or more races," who tend to support Trump slightly more.
+
 ```{r}
-
+#| label: fig-race
+#| fig-cap: The distribution of presidential preferences by race
+#| echo: false
+#| warning: false
+#| message: false
 ces2020 |>
   ggplot(aes(x = race, fill = voted_for)) +
-  geom_bar() +
-  coord_flip()
+  geom_bar(position = "dodge2") +
+  coord_flip() +
+  theme_minimal() +
+  labs(
+    x = "Race",
+    y = "Number of respondents",
+    fill = "Voted for"
+  )
 ```
 
-@fig-race_region shows the relationship between race, region, and voting preference.
+@fig-race_region shows the more detailed relationship between race, region, and voting preference.
 In the Northeast, Midwest, and West regions of the United States, there is a consistent pattern where individuals across almost all racial groups tend to show greater support for Biden over Trump.
@@
 However, it is evident that White individuals constitute a significantly larger portion of the population compared to other racial groups, thereby exerting a greater influence on voting outcomes.
+
 ```{r}
@@
 
-@fig-race_employ illustrates the relationship between region, employment status, and voting preferences for Trump and Biden.
+@fig-region shows the relationship between employment and voting preferences.
+Across various employment statuses, there is a consistent trend of higher support for Biden compared to Trump.
+It can be observed that individuals holding full-time jobs show the most disparity in support between the two candidates, with Biden gaining substantially more support than Trump.
+The support for Biden and Trump among those with other employment statuses is relatively similar, with the support for Biden slightly higher than for Trump.
+```{r}
+#| label: fig-region
+#| fig-cap: The distribution of presidential preferences by race
+#| echo: false
+#| warning: false
+#| message: false
+ces2020 |>
+  ggplot(aes(x = employ, fill = voted_for)) +
+  geom_bar(position = "dodge2") +
+  coord_flip() +
+  theme_minimal() +
+  labs(
+    x = "Employment status",
+    y = "Number of respondents",
+    fill = "Voted for"
+  )
+```
+
+@fig-region_employ illustrates a more detailed relationship between region, employment status, and voting preferences for Trump and Biden.
 Across all regions, people in full-time and part-time employment show a greater percentage of support for Biden than to Trump.
@@
 ```{r}
-#| label: fig-race_employ
+#| label: fig-region_employ
 #| fig-cap: The distribution of presidential preferences, by region and employment status

### 2024-03-12 paper/us_election_2020.qmd
small adjustment

@@
 We analyze the 2020 election data set from Cooperative Election Study (CES) [citation needed] and build a prediction model for individual voting preference.
-This allows us to discover trends and address potential political, economic, and societal issues to better reflect the needs and preferences of diverse communities.
+This allows us to discover trends and address potential political, economic, and societal situations that may cause the eventual winning for Biden.
 
@@
 Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
-Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set, which are race, region that they live, and employment status.
+Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set.We selected data features:race, region that they live, employment status, and who they voted for.
 The estimand in this paper is the number of people who support Trump and Biden in reality.
 However, it is difficult to measure the exact number of people who support Trump and Biden since there are millions of people in the United States and not all of them with the rights to vote would actually vote.
-Therefore, in this paper, we attempt to estimate the estimand using a logistic regression model which is trained using 2020 election data set from CES.
+Therefore, in this paper, we attempt to estimate the estimand using a logistic regression model which is trained using sample dataset from the 2020 election dataset from CES.
 
-We found that in the 2020 presidential election, Biden had strong support from racial groups including black, Hispanic, and Asian populations.
-Geographically, Biden gained greater support in the Northeast and West regions, while Trump secured more votes in the South.
-Additionally, both full-time and part-time workers, as well as students and those facing unemployment or layoffs, leaned towards Biden.
+The logistic regression model shows that in the 2020 presidential election, Biden has strong support from racial groups including black, Hispanic, and Asian populations.
+Geographically, Biden gains greater support in the Northeast and West regions, while Trump secured more votes in the South.
+Additionally, both full-time and part-time workers, as well as students and those facing unemployment or layoffs, lean towards Biden.
 
@@
   theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
   labs(
@@
 ```
-This bubble plot (@fig-race_employ_region) illustrates four variables: race, region, employment status, and voting preference.
+<!-- This bubble plot (@fig-race_employ_region) illustrates four variables: race, region, employment status, and voting preference.
 Darker dots indicate a higher number of people, with red representing Trump supporters and blue for Biden supporters.
@@
 In those purple dots, we found that mostly are from people who are either Native American or from the South.
+-->
 

### 2024-03-12 paper/us_election_2020.qmd
add discussion of race and ref

--- 2024-03-12 paper/us_election_2020.qmd
@@
 Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
-On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign.
+His winning was surprising and it led people to challenge the preconceived notions and reliability of pre-election polling data [citation needed].
+On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign [citation needed].
 He aimed to regain control from the Republican party.
-In the end, Biden won the election by 51.3% majority votes (@cnn_2020), which Trump questioned its credibility.
-Due to the COVID-19 pandemic in 2020, the vote system changed to in-mail voting instead of in-person voting, which was why Trump believed that some votes were stolen (@trump_stolenvote).
-Therefore, it is important for us to analyze why people voted for Biden and Trump in 2020 election and how various demographic, economic, and social factors may influence individuals' voting decisions.
-Perhaps then we could see why Biden eventually won.
-We analyze the 2020 election data set from Cooperative Election Study (CES) [citation needed] and build a prediction model for individual voting preference.
-This allows us to discover trends and address potential political, economic, and societal issues to better reflect the needs and preferences of diverse communities.
+In the end, Biden won the election by 51.3% majority votes [citation needed].
+It is important for us to understand how various demographic, economic, and social factors may influence individuals' voting decisions, which is why we decide to analyze the 2020 election data set and build a prediction model.
+This allows us to discover trends and address potential issues in society to better reflect the needs and preferences of diverse communities.
 
-In this paper, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study.
+In this paper, a logistic regression model is used to forecast the outcome of the 2020 election, with data from the Cooperative Election Study (CES)  [citation needed].
 Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
 Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set, which are race, region that they live, and employment status.
-The estimand in this paper is the number of people who support Trump and Biden in reality.
-However, it is difficult to measure the exact number of people who support Trump and Biden since there are millions of people in the United States and not all of them with the rights to vote would actually vote.
-Therefore, in this paper, we attempt to estimate the estimand using a logistic regression model which is trained using 2020 election data set from CES.
 
-We found that in the 2020 presidential election, Biden had strong support from racial groups including black, Hispanic, and Asian populations.
-Geographically, Biden gained greater support in the Northeast and West regions, while Trump secured more votes in the South.
-Additionally, both full-time and part-time workers, as well as students and those facing unemployment or layoffs, leaned towards Biden.
+**add： 4) what was done; 5) what was found after we finish the results section
 
@@
 @sec-result highlights the results of the predictions using tables and graphs.
-@sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, employment status, and the influence of COVID-19 and in-mail voting systems.
+@sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.
+
+## Estimand
+real vote_for biden or trump
 
@@
 ```
+
 ## Data Measurement
@@
 ## First discussion point
-race
-white
-- religion
 
-Biden: white, asian(trump covid), black, hispanic(trump建墙, no illegal immigration), other
-Trump: white, two or more races, 
-```{r}
-ces2020|>
-  filter(voted_for == "Biden") |>
-  select(race) |>
-  summary()
-```
-```{r}
-ces2020|>
-  filter(voted_for == "Trump") |>
-  select(race) |>
-  summary()
-```
+In our analysis, respondents of different races show varying levels of support, with a majority of blacks, Hispanics, and Asians supporting Biden, and a majority of Middle Easterners and multiracials supporting Trump.
+The results for whites are more evenly distributed, with about the same percentage supporting Biden and Trump.
+
+The reason for the majority of Hispanics supporting Biden may be due to the US-Mexico border wall that was built during Trump's reign.
+The wall was built over 452 miles, which replaced the old fence (@Rodriguez_2021).
+With this measure in place, Trump lost most of the Hispanic vote.
+Trump claims the wall reformed the immigration system and achieved the most secure southern border in US history.
+However, that wasn't true, and with it has come a surge in illegal border crossings.
+For Hispanics, Trump's long history of anti-immigrant rhetoric and this border wall have denied them the opportunity to seek asylum.
+While crossing the border illegally is not something to be promoted, it is the last hope for those living in dire straits.
+
+2020 is the age of pandemics, as Trump's phrase "Chinese virus" led to a large number of Asians starting to support Biden.
+This is an extremely anti-Asian statement, although Covid was first found in China, but it does not mean that it is the Chinese virus.
+Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community (@Reja_2021).
+The repeated use of the "Chinese Virus" by a president of the country has contributed to an environment of racial discrimination and hatred against Asians, which has directly led to more Asians supporting Biden, whose policies are more open and democratic, and who values racial equality more.
+
+Most white people vote relatively evenly, due to the fact that they are not affected by immigration or other policies.
+Whites hold a major voice and position in the US, most of the ideas and policies Trump proposes are favorable to whites.
+Therefore, he can gain support from most whites.
+However, there are some whites who want a democratic and free environment, and at the same time do not want to see racial discrimination and other phenomena, so they will choose to support Biden, who values equality.
 
@@
 maybe talk about employment?
+tax
 

### 2024-03-12 paper/us_election_2020.qmd
fix structure issue
added appendix

@@
 Perhaps then we could see why Biden eventually won.
-We analyze the 2020 election data set from Cooperative Election Study (CES) [citation needed] and build a prediction model for individual voting preference.
+We analyze the 2020 election data set from Cooperative Election Study (CES) (@citeCes2020) and build a prediction model for individual voting preference.
 This allows us to discover trends and address potential political, economic, and societal situations that may cause the eventual winning for Biden.
@@
 ## Data Source
-In this report, we use the 2020 Cooperative Election Study (CES) (@citeCes2020) as out primary dataset.
+In this report, we use the 2020 Cooperative Election Study (CES) (@citeCes2020) as our primary dataset.
 This is a long-established annual political survey of US.
@@
 
-raw_ces2020[1:5, 1:5] |>
-  kable()
+# raw_ces2020[1:5, 1:5] |>
+#   kable()
 ```
@@
 Firstly, for the variable "votereg" indicating whether a respondent is registered to vote, the measurement process involves relying on self-reported information from survey respondents.
-The US voter registration system is known to be inaccurate and inefficient.While efforts are made to ensure accuracy, there may be instances of misreporting or misunderstanding of voter registration status, leading to potential inaccuracies in the data.
+The US voter registration system is known to be inaccurate and inefficient.
+While efforts are made to ensure accuracy, there may be instances of misreporting or misunderstanding of voter registration status, leading to potential inaccuracies in the data.
 According to [@inaccurate], there are millions of voter registrations that are no longer valid or inaccurate.
@@
 Among many voters, voting for Trump became associated with characteristics such as being uneducated, backward-thinking, and anti-science.
-As a result, individuals who voted for him may have felt social pressure to conceal or lie about their support, potentially leading to underreporting of votes for Trump in the survey data.
+As a result, individuals who voted for him may have felt social pressure to conceal or lie about their support, potentially leading to under-reporting of votes for Trump in the survey data.
 
@@
 For instance, states like Missouri and Kentucky are often considered part of the Midwest but also share cultural and economic ties with the South.
-This complexity can make individuals accurately reporting thier region challenging.
+This complexity can make individuals accurately reporting their region challenging.
 
@@
 
-The dataset is cleaned by rename the column names, specify the class of the columns, and change the numbers in the table to the corresponding description in the codebook to improve the readability.
-In addition, the cleaned data removes NA employment status since there are only 34 rows, which is a small amount of missing value compared with 61000 rows.
-After cleaning, 43534 rows of data and 4 variables remain.
+The dataset is cleaned by renaming the column names, specifying the class of the columns, and changing the numbers in the table to the corresponding description in the codebook to improve the readability.
+In addition, NA employment status is removed in the cleaned data file since there are only 34 entries, which is a small amount of missing value compared with 61000 entries.
+After cleaning, 43534 rows of data with 4 data features remain.
 
@@
 
--------------------------------needs some explanation
-```{r}
-# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
-political_preferences1 <-
-  readRDS(file = here::here("models/political_preferences1.rds"))
+## Model Implication
+Figure # shows range of coefficient estimates of our model within the 90% probability.
+Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
+Therefore we created figure # with the x axis limited from -10 to 10.
 
-pp_check(political_preferences1) +
-  theme(legend.position = "bottom")
-```
+Combining figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+The estimates are significant if the intervals do not cross 0.
+The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
 
@@
   ggplot(aes(x = race, fill = voted_for)) +
-  geom_bar(position = "dodge2") +
+  geom_bar(position = "dodge") +
   coord_flip() +
@@
   ggplot(aes(x = employ, fill = voted_for)) +
-  geom_bar(position = "dodge2") +
+  geom_bar(position = "dodge") +
   coord_flip() +
@@
 ```
-<!-- This bubble plot (@fig-race_employ_region) illustrates four variables: race, region, employment status, and voting preference.
-Darker dots indicate a higher number of people, with red representing Trump supporters and blue for Biden supporters.
-Purple dots suggest similar support rates for both candidates, since blue and red makes purple in a 1:1 ratio.
-We can see that the darker dots are mostly in White, Black, Hispanic communities for full-time, part-time, or retired individuals.
-The darker dots are all blue, which indicates stronger support for Biden.
-It can also be noted that there are very few entirely red dots, which means that there is no significant disparities in voting percentages between Trump and Biden even among those groups which partially supported Trump.
-In those purple dots, we found that mostly are from people who are either Native American or from the South.
--->
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in @tbl-modelresults1.
 
@@
 ```
-Our results generally matches our justification.
-To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+Our results generally matches our expectation To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
 In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.
@@
 
-Figure # shows range of coefficient estimates of our model within the 90% probability.
-Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
-Therefore we created figure # with the x axis limited from -10 to 10.
-
-Combing figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
-The estimates are significant if the intervals do not cross 0.
-The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-modelresults1
-#| fig-cap: "Credible intervals for predictors of support for Biden 1"
-
-modelplot(political_preferences1, conf_level = 0.9) +
-  labs(x = "90% credibility interval")
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-modelresults2
-#| fig-cap: "Credible intervals for predictors of support for Biden 2"
-# Create the model plot
-model_plot <- modelplot(political_preferences1, conf_level = 0.9)
-
-# Modify the x-axis limits
-model_plot + xlim(-5, 5) +  # Adjust the limits as needed
-  labs(x = "90% Credibility Interval")
-```
+\newpage
 
@@
 
-In our analysis, respondents of different races show varying levels of support, with a majority of blacks, Hispanics, and Asians supporting Biden, and a majority of Middle Easterners and multiracials supporting Trump.
+In our analysis, respondents of different races show varying levels of support, with a majority of blacks, Hispanics, and Asians supporting Biden, and a majority of Native Americans and multi-racials supporting Trump.
 The results for whites are more evenly distributed, with about the same percentage supporting Biden and Trump.
@@
 2020 is the age of pandemics, as Trump's phrase "Chinese virus" led to a large number of Asians starting to support Biden.
-This is an extremely anti-Asian statement, although Covid was first found in China, but it does not mean that it is the Chinese virus.
+This is an extremely anti-Asian statement: although COVID-19 was first found in China, but it does not mean that virus was from China.
 Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community (@Reja_2021).
@@
 Therefore, he can gain support from most whites.
-However, there are some whites who want a democratic and free environment, and at the same time do not want to see racial discrimination and other phenomena, so they will choose to support Biden, who values equality.
+However, there are some whites who want a democratic and equal environment, and at the same time do not want to see racial discrimination and other phenomena, so they will choose to support Biden, who values equality.
 
@@
 Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes.
-This support is particularly evident in notable cities within these regions, driven by various factors including liberal ideals and progressive policies.
+This support is particularly evident in cities within these regions, driven by various factors including liberal ideals and progressive policies.
 For instance, states like New York and Massachusetts support Biden due to their liberal-leaning populations, diverse demographics, and emphasis on social justices.
@@
 ## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-post_dist, we implement a posterior distribution.
+This compares who people voted for in reality with the prediction results from the posterior distribution from our logistic regression model.
+It can be observed that the posterior distribution fits perfectly with the actual data, it suggests that the model accurately captures the observed data patterns.
+So the posterior is able to generate simulated data that closely resembles the actual data (@bayes_post).
+This is a positive sign because it indicates that our logistic regression model is a good representation of the actual voting preferences in the 2020 election data.
 
 ```{r}
-#| eval: true
+#| label: fig-post_dist
+#| fig-cap: Posterior distribution for logistic regression model 
 #| echo: false
+#| warning: false
 #| message: false
+
+pp_check(political_preferences1) +
+  theme(legend.position = "bottom")
+```
+
+@fig-post_prior compares the posterior with the prior.
+This compares the prior distribution of parameters with the posterior distribution of parameters in our logistic regression model.
+We can see that majority of the model parameters do not change even after data are taken into account.
+This shows that the observed data matches with our initial belief and expectation about the voting preferences for 2020 presidential election.
+However, for "raceOther", the posterior distribution shifts from its prior after we input observed data.
+This is likely suggesting that the observed data for "raceOther" strongly contradicts our initial belief.
+Yet, this is not a big problem since the percentage of the racial group "raceOther" is 0.86% (473/43534 from @tbl-summary) in our dataset.
+
+```{r}
+#| label: fig-post_prior
+#| fig-cap: Comparing the posterior with the prior 
+#| echo: false
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+#| message: false
+
+#### Read data ####
+analysis_data <- read_csv(here::here("data/analysis_data/cleaned_ces2020.csv"))
+
+# Convert variables to factors
+analysis_data$race <- factor(analysis_data$race)
+analysis_data$region <- factor(analysis_data$region)
+analysis_data$employ <- factor(analysis_data$employ)
+
+# Create voted_for variable in binary form
+analysis_data$voted_for_binary <- ifelse(analysis_data$voted_for == "Biden", 1, 0)
+
+# Model 1 for n = 1000
+set.seed(123)
+
+ces2020_reduced <- 
+  analysis_data |> 
+  slice_sample(n = 1000)
+
+posterior_vs_prior(political_preferences1) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
+## Credibility interval
+
+```{r}
+#| label: fig-conf
+#| fig-cap: Comparing the posterior with the prior 
+#| echo: false
+#| warning: false
+#| message: false
+plot(
+  political_preferences1,
+  "areas"
+)
+```
+```{r}
+#| label: fig-conf_lim
+#| fig-cap: Comparing the posterior with the prior 
+#| echo: false
+#| warning: false
+#| message: false
+#| 
+model_plot <- plot(
+  political_preferences1,
+  "areas"
+)
+# Modify the x-axis limits
+model_plot + xlim(-10, 10) +  # Adjust the limits as needed
+  labs(x = "90% Credibility Interval")
+```
+## Credibility Interval
+
+```{r}
+# #| echo: false
+# #| eval: true
+# #| warning: false
+# #| message: false
+# #| label: fig-modelresults1
+# #| fig-cap: "Credible intervals for predictors of support for Biden 1"
 # 
-# pp_check(first_model) +
-#   theme_classic() +
-#   theme(legend.position = "bottom")
+# modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
+#   labs(x = "90% credibility interval")
+```
+
+```{r}
+# #| echo: false
+# #| eval: true
+# #| warning: false
+# #| message: false
+# #| label: fig-modelresults2
+# #| fig-cap: "Credible intervals for predictors of support for Biden 2"
+# # Create the model plot
+# model_plot <- modelplot(political_preferences1, conf_level = 0.9)
 # 
-# posterior_vs_prior(first_model) +
-#   theme_minimal() +
-#   scale_color_brewer(palette = "Set1") +
-#   theme(legend.position = "bottom") +
-#   coord_flip()
+# # Modify the x-axis limits
+# model_plot + xlim(-5, 5) +  # Adjust the limits as needed
+#   labs(x = "90% Credibility Interval")
 ```

### 2024-03-12 paper/us_election_2020.qmd
last changes

--- 2024-03-12 paper/us_election_2020.qmd
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper delves into the dynamics of voter turnout of the 2020 United States presidential election.
+Utilizing dataset from the Cooperate Election Study (CES2020), we employ logistic regression analysis to explore the influence of the voter's race, region, and employment on their vote for presidential candidate.
+Our findings reveal distinct voting patterns among different demographic groups, with minorities showing strong support for Biden, the South predominantly favored Trump, and individuals reliant on unemployment benefits preferred Biden.
+These insights stress the need for customized outreach and policies to enhance voter engagement across diverse U.S.
+communities."
 format: pdf
+toc: true
 number-sections: true
@@
 ```
-
 ## Data Measurement
@@
 In addition, the cleaned data removes NA employment status since there are only 34 rows, which is a small amount of missing value compared with 61000 rows.
-After cleaning, 43534 rows of data and 4 variables remain.
+After []
 
-The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), and `kableExtra` (@citeKableExtra).
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), `testthat` (@citetestthat) and `kableExtra` (@citeKableExtra).
 @tbl-clean-data shows a preview of the cleaned dataset.
@@
 
-@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset.
-As we can see from the table, there are more people who support Biden.
-Respondents covered a wide range of races, with white people being the most heavily represented.
-Also, CES data came from a variety of locations, but the majority came from the southern region of the United States.
-The employment status of those who completed the survey varied, with most of them being full-time or retired.
+@tbl-summary is a summary of the cleaned data, showing detailed statistics about the dataset. ***add detail***
 ```{r}
@@
 
-## Model set-up
+## Model Set-up
 
@@
 
-### Model justification
+### Model Justification
 
@@
 ```
-This bubble plot (@fig-race_employ_region) illustrates four variables: race, region, employment status, and voting preference.
-Darker dots indicate a higher number of people, with red representing Trump supporters and blue for Biden supporters.
-Purple dots suggest similar support rates for both candidates, since blue and red makes purple in a 1:1 ratio.
-We can see that the darker dots are mostly in White, Black, Hispanic communities for full-time, part-time, or retired individuals.
-The darker dots are all blue, which indicates stronger support for Biden.
-It can also be noted that there are very few entirely red dots, which means that there is no significant disparities in voting percentages between Trump and Biden even among those groups which partially supported Trump.
-In those purple dots, we found that mostly are from people who are either Native American or from the South.
 
 ## Model Results
-
-Our results are summarized in @tbl-modelresults.
 
@@
 ```
-Our results generally matches our justification.
+Our results are summarized in @tbl-modelresults1.Our results generally matches our justification.
 To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
@@
 
-Figure # shows range of coefficient estimates of our model within the 90% probability.
+@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability.
 Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
@@
 
-Combing figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
 The estimates are significant if the intervals do not cross 0.
@@
 ## First discussion point
+race
+white
+- religion
 
-In our analysis, respondents of different races show varying levels of support, with a majority of blacks, Hispanics, and Asians supporting Biden, and a majority of Middle Easterners and multiracials supporting Trump.
-The results for whites are more evenly distributed, with about the same percentage supporting Biden and Trump.
-
-The reason for the majority of Hispanics supporting Biden may be due to the US-Mexico border wall that was built during Trump's reign.
-The wall was built over 452 miles, which replaced the old fence (@Rodriguez_2021).
-With this measure in place, Trump lost most of the Hispanic vote.
-Trump claims the wall reformed the immigration system and achieved the most secure southern border in US history.
-However, that wasn't true, and with it has come a surge in illegal border crossings.
-For Hispanics, Trump's long history of anti-immigrant rhetoric and this border wall have denied them the opportunity to seek asylum.
-While crossing the border illegally is not something to be promoted, it is the last hope for those living in dire straits.
-
-2020 is the age of pandemics, as Trump's phrase "Chinese virus" led to a large number of Asians starting to support Biden.
-This is an extremely anti-Asian statement, although Covid was first found in China, but it does not mean that it is the Chinese virus.
-Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community (@Reja_2021).
-The repeated use of the "Chinese Virus" by a president of the country has contributed to an environment of racial discrimination and hatred against Asians, which has directly led to more Asians supporting Biden, whose policies are more open and democratic, and who values racial equality more.
-
-Most white people vote relatively evenly, due to the fact that they are not affected by immigration or other policies.
-Whites hold a major voice and position in the US, most of the ideas and policies Trump proposes are favorable to whites.
-Therefore, he can gain support from most whites.
-However, there are some whites who want a democratic and free environment, and at the same time do not want to see racial discrimination and other phenomena, so they will choose to support Biden, who values equality.
+Biden: white, asian(trump covid), black, hispanic(trump建墙, no illegal immigration), other
+Trump: white, two or more races, 
+```{r}
+ces2020|>
+  filter(voted_for == "Biden") |>
+  select(race) |>
+  summary()
+```
+```{r}
+ces2020|>
+  filter(voted_for == "Trump") |>
+  select(race) |>
+  summary()
+```
 
@@
 maybe talk about employment?
-tax
 
@@
 
-## Weaknesses and next steps
+## Weaknesses and Next Steps
 

### 2024-03-12 paper/us_election_2020.qmd

--- 2024-03-12 paper/us_election_2020.qmd
@@
 
-The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), and `kableExtra` (@citeKableExtra).
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), `testthat` (@citetestthat) and `kableExtra` (@citeKableExtra).
 @tbl-clean-data shows a preview of the cleaned dataset.
@@
 
-Our results are summarized in @tbl-modelresults1.
-
 ```{r}
@@
 ```
-Our results generally matches our expectation To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+Our results are summarized in @tbl-modelresults1.
+Our results generally matches our expectation.
+To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
 In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.
@@
 
+@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability.
+Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
+Therefore we created figure # with the x axis limited from -10 to 10.
+
+Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+The estimates are significant if the intervals do not cross 0.
+The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
+
 \newpage
@@
 
-## First discussion point
+## Racial Variations
 
@@
 
-## Third discussion point
+## Employment Variations
 

### 2024-03-12 paper/us_election_2020.qmd
changes

@@
 
-## Model Implication
-Figure # shows range of coefficient estimates of our model within the 90% probability.
-Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
-Therefore we created figure # with the x axis limited from -10 to 10.
-
-Combining figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
-The estimates are significant if the intervals do not cross 0.
-The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
-
 # Results {#sec-result}
@@
 
-@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability.
+@fig-modelresults1 (see @sec-credibility-interval) inshows range of coefficient estimates of our model within the 90% probability.
 Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
@@
 ```
-## Credibility Interval
+## Credibility Interval {#sec-credibility-interval}
 
 ```{r}
-# #| echo: false
-# #| eval: true
-# #| warning: false
-# #| message: false
-# #| label: fig-modelresults1
-# #| fig-cap: "Credible intervals for predictors of support for Biden 1"
-# 
-# modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
-#   labs(x = "90% credibility interval")
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of support for Biden 1"
+
+modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
+ labs(x = "90% credibility interval")
 ```
@@
 ```{r}
-# #| echo: false
-# #| eval: true
-# #| warning: false
-# #| message: false
-# #| label: fig-modelresults2
-# #| fig-cap: "Credible intervals for predictors of support for Biden 2"
-# # Create the model plot
-# model_plot <- modelplot(political_preferences1, conf_level = 0.9)
-# 
-# # Modify the x-axis limits
-# model_plot + xlim(-5, 5) +  # Adjust the limits as needed
-#   labs(x = "90% Credibility Interval")
+ #| echo: false
+ #| eval: true
+ #| warning: false
+ #| message: false
+ #| label: fig-modelresults2
+ #| fig-cap: "Credible intervals for predictors of support for Biden 2"
+ # Create the model plot
+ model_plot <- modelplot(political_preferences1, conf_level = 0.9)
+
+ # Modify the x-axis limits
+ model_plot + xlim(-10, 10) +  # Adjust the limits as needed
+   labs(x = "90% Credibility Interval")
 ```

### 2024-03-12 paper/us_election_2020.qmd
model implication

@@
 date-format: long
-abstract: "This paper delves into the dynamics of voter turnout of the 2020 United States presidential election.
-Utilizing dataset from the Cooperate Election Study (CES2020), we employ logistic regression analysis to explore the influence of the voter's race, region, and employment on their vote for presidential candidate.
-Our findings reveal distinct voting patterns among different demographic groups, with minorities showing strong support for Biden, the South predominantly favored Trump, and individuals reliant on unemployment benefits preferred Biden.
-These insights stress the need for customized outreach and policies to enhance voter engagement across diverse U.S.
-communities."
+abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 format: pdf
-toc: true
 number-sections: true
@@
 
-The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), `testthat` (@citetestthat) and `kableExtra` (@citeKableExtra).
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), and `kableExtra` (@citeKableExtra).
 @tbl-clean-data shows a preview of the cleaned dataset.
@@
 
-## Model Set-up
+## Model set-up
 
@@
 
-### Model Justification
+### Model justification
 
@@
 Additionally, educated and liberal-leaning working professionals may prioritize issues such as healthcare, climate change, and social justice, aligning them with Biden's platform.
+
+## Model Implication
+In @fig-post_dist, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns.
+This indicates the accuracy of our model's voting preference prediction to the 2020 election data.
+Also, @fig-post_prior compares the posterior to the prior, which shows minimal parameter changes except for the parameter "raceOther".
+The discrepancy for the parameter "raceOther" is not critical due to the low representation of "raceOther" in the dataset.
+
+Figure # shows range of coefficient estimates of our model within the 90% probability.
+Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
+Therefore we created figure # with the x axis limited from -10 to 10.
+
+Combining figure # and figure #, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+The estimates are significant if the intervals do not cross 0.
+The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
+
+The trace plot in @fig-mcmc-1 does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-mcmc-2), we can observe that everything is close to 1, and no more than 1.05.
 
@@
 
+Our results are summarized in @tbl-modelresults1.
+
 ```{r}
@@
 ```
-Our results are summarized in @tbl-modelresults1.
-Our results generally matches our expectation.
-To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+Our results generally matches our expectation To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
 In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.
@@
 
-@fig-modelresults1 (see @sec-credibility-interval) inshows range of coefficient estimates of our model within the 90% probability.
-Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
-Therefore we created figure # with the x axis limited from -10 to 10.
-
-Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
-The estimates are significant if the intervals do not cross 0.
-The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
-
 \newpage
@@
 
-## Racial Variations
+## First discussion point
 
@@
 
-## Employment Variations
+## Third discussion point
 
@@
 
-## Weaknesses and Next Steps
+## Weaknesses and next steps
 
@@
 ```
-## Credibility Interval {#sec-credibility-interval}
 
@@
 # Modify the x-axis limits
- model_plot + xlim(-10, 10) +  # Adjust the limits as needed
+model_plot + xlim(-5, 5) +  # Adjust the limits as needed
   labs(x = "90% Credibility Interval")
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-trace is a trace plot.
+It shows if there is existence of signs that the our model runs into issues.
+We observe lines that are horizontal and oscillating, and have overlaps between the chains.
+This suggests that there is nothing strange in this trace plot.
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-rhat is a Rhat plot.
+It compares the variability within each chain to the variability between chains in MCMC.
+Ideally, we want Rhat to be close to 1, which indicates that the chains have converged to the same distribution.
+We can observe that our Rhat plot are all close to 1, and no more than 1.05.
+This is a positive sign because it suggests that the MCMC algorithm has reached convergence for our model.
 
@@
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| label: fig-trace
+#| fig-cap: "Trace plot"
 
  plot(political_preferences1, "trace")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-rhat
+#| fig-cap: "Rhat plot"
 

### 2024-03-12 paper/us_election_2020.qmd
change

--- 2024-03-12 paper/us_election_2020.qmd
@@
 
+## Model Implication
+In @fig-post_dist, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns.
+This indicates the accuracy of our model's voting preference prediction to the 2020 election data.
+Also, @fig-post_prior compares the posterior to the prior, which shows minimal parameter changes except for the parameter "raceOther".
+The discrepancy for the parameter "raceOther" is not critical due to the low representation of "raceOther" in the dataset.
+
+The trace plot in @fig-mcmc-1 does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-mcmc-2), we can observe that everything is close to 1, and no more than 1.05.
+
 # Results {#sec-result}
@@
 
-@fig-modelresults1 (see @sec-credibility-interval) inshows range of coefficient estimates of our model within the 90% probability.
+@fig-modelresults1 (see @sec-credibility-interval) shows range of coefficient estimates of our model within the 90% probability.
 Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
@@
 
-Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+Combining @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
 The estimates are significant if the intervals do not cross 0.
@@
 
-maybe talk about employment?
-tax
+will write later
 
@@
 
-## Credibility interval
-
-```{r}
-#| label: fig-conf
-#| fig-cap: Comparing the posterior with the prior 
-#| echo: false
-#| warning: false
-#| message: false
-plot(
-  political_preferences1,
-  "areas"
-)
-```
-```{r}
-#| label: fig-conf_lim
-#| fig-cap: Comparing the posterior with the prior 
-#| echo: false
-#| warning: false
-#| message: false
-#| 
-model_plot <- plot(
-  political_preferences1,
-  "areas"
-)
-# Modify the x-axis limits
-model_plot + xlim(-10, 10) +  # Adjust the limits as needed
-  labs(x = "90% Credibility Interval")
-```
 ## Credibility Interval {#sec-credibility-interval}
@@
 
-modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
+modelplot(political_preferences1, conf_level = 0.90, size = 0.1) +
   labs(x = "90% credibility interval")

### 2024-03-12 paper/us_election_2020.qmd
minor changes

@@
 Logistic regression is a great choice since it is used to predict binary outcomes, such as election results (Trump or Biden).
-Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set.We selected data features:race, region that they live, employment status, and who they voted for.
+Our analysis focuses on estimating the likelihood of victory for either Trump or Biden, based on various demographic, geographic, and socioeconomic factors captured in the CES data set.We selected data features: race, region that they live, employment status, and who they voted for.
 The estimand in this paper is the number of people who support Trump and Biden in reality.
@@
 
-# raw_ces2020[1:5, 1:5] |>
-#   kable()
+raw_ces2020[1:5, 1:5] |>
+  kable()
 ```
@@
 
-### Model Justification
+## Model Justification
 
@@
 
-The trace plot in @fig-mcmc-1 does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-mcmc-2), we can observe that everything is close to 1, and no more than 1.05.
+The trace plot in @fig-trace does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-rhat), we can observe that everything is close to 1, and no more than 1.05.
 
@@
 
-## Diagnostics
+## Markov chain Monte Carlo Convergence Check
 

### 2024-03-13 paper/us_election_2020.qmd
new page for intro
fix citation brackets

@@
 
+\newpage
+
 # Introduction
@@
 He aimed to regain control from the Republican party.
-In the end, Biden won the election by 51.3% majority votes (@cnn_2020), which Trump questioned its credibility.
-Due to the COVID-19 pandemic in 2020, the vote system changed to in-mail voting instead of in-person voting, which was why Trump believed that some votes were stolen (@trump_stolenvote).
+In the end, Biden won the election by 51.3% majority votes [@cnn_2020], which Trump questioned its credibility.
+Due to the COVID-19 pandemic in 2020, the vote system changed to in-mail voting instead of in-person voting, which was why Trump believed that some votes were stolen [@trump_stolenvote].
 Therefore, it is important for us to analyze why people voted for Biden and Trump in 2020 election and how various demographic, economic, and social factors may influence individuals' voting decisions.
 Perhaps then we could see why Biden eventually won.
-We analyze the 2020 election data set from Cooperative Election Study (CES) (@citeCes2020) and build a prediction model for individual voting preference.
+We analyze the 2020 election data set from Cooperative Election Study (CES) [@citeCes2020] and build a prediction model for individual voting preference.
 This allows us to discover trends and address potential political, economic, and societal situations that may cause the eventual winning for Biden.
@@
 ## Data Source
-In this report, we use the 2020 Cooperative Election Study (CES) (@citeCes2020) as our primary dataset.
+In this report, we use the 2020 Cooperative Election Study (CES) [@citeCes2020] as our primary dataset.
 This is a long-established annual political survey of US.
@@
 
-The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `here` (@citeHere), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModleSummary), `ggplot2` (@citeGgplot2), `knitr` (@citeKnitr), `marginaleffects` (@citeMarginalEffects), `plotly` (@citePlotly), `tibble` (@citeTibble), `margins` (@citeMargins), `testthat` (@citetestthat) and `kableExtra` (@citeKableExtra).
+The cleaned data will be analyzed and performed using R [@citeR] with `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat] and `kableExtra` [@citeKableExtra].
 @tbl-clean-data shows a preview of the cleaned dataset.
@@
 The reason for the majority of Hispanics supporting Biden may be due to the US-Mexico border wall that was built during Trump's reign.
-The wall was built over 452 miles, which replaced the old fence (@Rodriguez_2021).
+The wall was built over 452 miles, which replaced the old fence [@Rodriguez_2021].
 With this measure in place, Trump lost most of the Hispanic vote.
@@
 This is an extremely anti-Asian statement: although COVID-19 was first found in China, but it does not mean that virus was from China.
-Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community (@Reja_2021).
+Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community [@Reja_2021].
 The repeated use of the "Chinese Virus" by a president of the country has contributed to an environment of racial discrimination and hatred against Asians, which has directly led to more Asians supporting Biden, whose policies are more open and democratic, and who values racial equality more.
@@
 It can be observed that the posterior distribution fits perfectly with the actual data, it suggests that the model accurately captures the observed data patterns.
-So the posterior is able to generate simulated data that closely resembles the actual data (@bayes_post).
+So the posterior is able to generate simulated data that closely resembles the actual data [@bayes_post].
 This is a positive sign because it indicates that our logistic regression model is a good representation of the actual voting preferences in the 2020 election data.

### 2024-03-15 paper/us_election_2020.qmd
unemployment

@@
 date-format: long
-abstract: "This paper delves into the dynamics of voter turnout of the 2020 United States presidential election.
+abstract: "This paper examines the dynamics of voter turnout of the 2020 United States presidential election.
 Utilizing dataset from the Cooperate Election Study (CES2020), we employ logistic regression analysis to explore the influence of the voter's race, region, and employment on their vote for presidential candidate.
@@
 
-will write later
+Individuals employed part-time, laid-off, or unemployed demonstrate a notable support towards Biden, a trend likely attributed to Biden's alignment with policies favoring these groups, such as enhanced benefits and support programs [@williams_2020].
+For example, Biden and his party advocate for extending unemployment benefits, providing relief for laid-off workers, and bolstering job creation initiatives to address economic challenges faced by these individuals.
+
+Furthermore, students are strongly interested in Biden.
+The Democratic party's advocacy for liberal rights, racial equality, and healthcare reform resonate with many students' values and priorities [@hess_2020].
+Biden's emphasis on addressing issues like student debt, access to affordable education, and healthcare affordability also appeals to students as these issues are highly related to them.
+Additionally, Biden's support for racial equality and social justice initiatives aligns with the progressive values often embraced by college students.
 

### 2024-03-16 paper/us_election_2020.qmd
some edits

@@
 abstract: "This paper examines the dynamics of voter turnout of the 2020 United States presidential election.
-Utilizing dataset from the Cooperate Election Study (CES2020), we employ logistic regression analysis to explore the influence of the voter's race, region, and employment on their vote for presidential candidate.
-Our findings reveal distinct voting patterns among different demographic groups, with minorities showing strong support for Biden, the South predominantly favored Trump, and individuals reliant on unemployment benefits preferred Biden.
+Utilizing dataset from the Cooperate Election Study (CES2020), we employ logistic regression analysis to explore the influence of the voter's race, region, and employment on their vote for presidential candidates, Biden and Trump.
+Our findings reveal distinct voting patterns among different demographic groups, with minorities showing strong support for Biden, the South favored Trump, and individuals working or reliant on unemployment benefits preferred Biden.
 These insights stress the need for customized outreach and policies to enhance voter engagement across diverse U.S.
@@
 # Introduction
-Four years ago, the United States once again was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
-The Democratic and Republican parties are represented by Donald Trump and Joe Biden respectively.
-Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
-On the other hand, Joe Biden, the former vice-president under Barack Obama's administration from 2008 to 2016, led the Democratic campaign.
+Four years ago, the United States was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
+The Democratic and Republican parties are represented by Donald Trump and Joe Biden respectively [@wiki2020].
+Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton [@result2016].
+On the other hand, Joe Biden led the Democratic campaign.
 He aimed to regain control from the Republican party.
@@
 Perhaps then we could see why Biden eventually won.
-We analyze the 2020 election data set from Cooperative Election Study (CES) [@citeCes2020] and build a prediction model for individual voting preference.
-This allows us to discover trends and address potential political, economic, and societal situations that may cause the eventual winning for Biden.
+We analyze the 2020 election data set from Cooperative Election Study (CES) [@citeCes2020].
+CES is a national online survey conducted before and after United States presidential elections [@wiki_ces].
+We build a prediction model for individual voting preference using dataset from CES 2020 elections.
+This allows us to discover trends and address potential political, economic, and societal situations that may cause the eventual winning for Biden in 2020.
 
@@
 
-The logistic regression model shows that in the 2020 presidential election, Biden has strong support from racial groups including black, Hispanic, and Asian populations.
+The logistic regression model shows that in the 2020 presidential election, Biden has strong support from minority racial groups including black, Hispanic, and Asian populations.
 Geographically, Biden gains greater support in the Northeast and West regions, while Trump secured more votes in the South.
@@
 
-1. votereg: whether the respondent is registered to vote.
+1. votereg: whether the respondent is registered to vote;
 
-2. CC20_410: the presidential candidate the respondent voted for.
+2. CC20_410: the presidential candidate the respondent voted for;
 
-3. race: the census region where the respondent lives.
+3. region: the census region where the respondent lives; options are "Northeast", "Midwest", "South", and "West".
 
-4. region: the racial or ethnic group of the respondent.
+4. race: the racial or ethnic group of the respondent; options are "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other".
 
-5. employ: the current employment status of the respondent.
+5.
+employ: the current employment status of the respondent; options are "Full-time", "Part-time", "Temporarily laid off", "Unemployed", "Retired", "Permanently disabled", "Homemaker", "Student", and "Other".
 
@@
 ## Model Implication
-In @fig-post_dist, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns.
+In @fig-post_dist in the Appendix, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns.
 This indicates the accuracy of our model's voting preference prediction to the 2020 election data.
@@
 
-The trace plot in @fig-trace does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-rhat), we can observe that everything is close to 1, and no more than 1.05.
+The trace plot in @fig-trace does not suggest anything out of the ordinary.
+Also, with the Rhat plot (@fig-rhat), we can observe that everything is close to 1, and no more than 1.05, which shows the great convergence of Markov chain Monte Carlo for our model.
 
@@
   theme(legend.position = "bottom")
-```
-
-```{r}
-#| label: fig-race_employ_region
-#| fig-cap: "The distribution of presidential preferences, by race, region and employment status"
-#| echo: false
-#| warning: false
-#| message: false
-#| include: false
-
-# plot_ly(x=ces2020$race, y=ces2020$region, z=ces2020$employ, colors = c("red", "blue")) %>% 
-#   add_markers(color = ces2020$voted_for, opacity = 0.03, size = 0.4) %>%
-#   layout(xaxis = list(title = 'Race'), yaxis = list(title = 'Region'), zaxis = list(title = 'Employment Status')) %>%
-#   layout(xaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
-#          yaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
-#          zaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)))
 ```

### 2024-03-16 paper/us_election_2020.qmd
some edits

@@
 @sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, employment status, and the influence of COVID-19 and in-mail voting systems.
+Statistical programming language R [@citeR] is used in this report, with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat] and `kableExtra` [@citeKableExtra].
 
@@
 
-1. votereg: whether the respondent is registered to vote;
+1. votereg: whether the respondent is registered to vote; numeric numbers starting from 1 correspond to options "Yes", "No", and "Don't know", respectively.
 
-2. CC20_410: the presidential candidate the respondent voted for;
+2.
+CC20_410: the presidential candidate the respondent voted for; numeric numbers starting from 1 correspond to  options "Joe Biden (Democrat)", "Donald J.
+Trump (Republican)", "Other", "I did not vote in this race", "I did not vote", "Not sure", respectively.
 
-3. region: the census region where the respondent lives; options are "Northeast", "Midwest", "South", and "West".
+3. region: the census region where the respondent lives; numeric numbers starting from 1 correspond to options "Northeast", "Midwest", "South", and "West", respectively.
 
-4. race: the racial or ethnic group of the respondent; options are "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other".
+4.
+race: the racial or ethnic group of the respondent; numeric numbers starting from 1 correspond to options "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other", respectively.
 
 5.
-employ: the current employment status of the respondent; options are "Full-time", "Part-time", "Temporarily laid off", "Unemployed", "Retired", "Permanently disabled", "Homemaker", "Student", and "Other".
+employ: the current employment status of the respondent; numeric numbers starting from 1 correspond to options "Full-time", "Part-time", "Temporarily laid off", "Unemployed", "Retired", "Permanently disabled", "Homemaker", "Student", and "Other", respectively.
 
@@
 After cleaning, 43534 rows of data with 4 data features remain.
-
-The cleaned data will be analyzed and performed using R [@citeR] with `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat] and `kableExtra` [@citeKableExtra].
 @tbl-clean-data shows a preview of the cleaned dataset.

### 2024-03-16 paper/us_election_2020.qmd
some edits

@@
 
-We expect a positive relationship between individuals of Black, Asian, and Hispanic ethnicities and support for Biden.
-This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall.
-These groups are more likely to align with Biden's policies, which prioritize inclusivity and diversity.
+We expect a positive relationship between individuals of Black, Asian, and Hispanic ethnicities and their support for Biden.
+This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall [@trump_wall].
+These groups are more likely to align with Biden's policies, which prioritize inclusion and diversity [@biden_inclusion].
 White individuals with traditional family values and conservative leanings tend to support Trump.
@@
 ## Model Implication
-In @fig-post_dist in the Appendix, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns.
+For posterior predictive checks, in @fig-post_dist, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns.
 This indicates the accuracy of our model's voting preference prediction to the 2020 election data.
@@
 
+More detailed explanation of each plot can be found in -@sec-model-details.
+
 # Results {#sec-result}
@@
 @fig-race shows the relationship between race and voting preference.
-Overall, Biden gets more support from most racial groups, except for Native Americans and people of "two or more races," who tend to support Trump slightly more.
+Overall, Biden gets more support from most racial groups, except for "Native Americans" and people of "two or more races," who tend to support Trump slightly more.
 
@@
 Hispanic races on average are also more likely to vote for Biden.
+We notice that Native Americans support Trump more with an estimated coefficient of -2.791.
 We observe an outlier, individuals with race "other" has a 37.999 higher log-odds of supporting Biden compared to the reference group.
 
-Voters preference for candidates also vary by regions and their employment status.
-Biden has more supports in the Northeast and West region while Trump gains a majority of his votes from the South.
+Voters preference for candidates also vary by regions.
+Biden has more supports in the Northeast (estimated coefficient of 0.436) and West region (estimated coefficient of 0.137) while Trump gains a majority of his votes from the South (estimated coefficient of -0.161).
+
+Individuals' employment statuses also have effects on voting preferences.
 As anticipated, students exhibit strong support for Biden.
-Additionally, individuals who are laid off, unemployed, or employed part-time, potentially reliant on social benefits, also prefer for Biden.
+Additionally, individuals who are employed part-time, laid off, or unemployed who potentially may be reliant on social benefits, also prefer for Biden.
 
@@
 Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
-Therefore we created figure # with the x axis limited from -10 to 10.
+Therefore we created @fig-modelresults2 with the x axis limited from -10 to 10.
 
@@
 
-In our analysis, respondents of different races show varying levels of support, with a majority of blacks, Hispanics, and Asians supporting Biden, and a majority of Native Americans and multi-racials supporting Trump.
-The results for whites are more evenly distributed, with about the same percentage supporting Biden and Trump.
+In our analysis, respondents of different races show varying levels of support, with a majority of Black, Hispanic, and Asian people supporting Biden, and a majority of Native Americans and multi-racials supporting Trump.
+The results for Whites are more evenly distributed, with approximately similar percentage of people supporting Biden and Trump.
 
@@
 The wall was built over 452 miles, which replaced the old fence [@Rodriguez_2021].
-With this measure in place, Trump lost most of the Hispanic vote.
-Trump claims the wall reformed the immigration system and achieved the most secure southern border in US history.
-However, that wasn't true, and with it has come a surge in illegal border crossings.
-For Hispanics, Trump's long history of anti-immigrant rhetoric and this border wall have denied them the opportunity to seek asylum.
-While crossing the border illegally is not something to be promoted, it is the last hope for those living in dire straits.
+With this measure in place, Trump lost most of the Hispanic votes.
+Trump claimed the wall reformed the immigration system and achieved the most secure southern border in US history.
+However, that was not true, and with it had come a surge in illegal border crossings [@trump_wall], which overall made Hispanic people dissatisfied with Trump's decisions and ruling.
 
-2020 is the age of pandemics, as Trump's phrase "Chinese virus" led to a large number of Asians starting to support Biden.
-This is an extremely anti-Asian statement: although COVID-19 was first found in China, but it does not mean that virus was from China.
+As COVID-19 pandemics spreaded, Trump repeatedly called it "Chinese virus" [@trump_virus].
+This obviously led to a large number of Asians, especially Chinese people, feel targeted becuase it is an extremely anti-Asian statement: although COVID-19 was first found in China, but it does not mean that virus was from China.
 Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community [@Reja_2021].
-The repeated use of the "Chinese Virus" by a president of the country has contributed to an environment of racial discrimination and hatred against Asians, which has directly led to more Asians supporting Biden, whose policies are more open and democratic, and who values racial equality more.
+The repeated use of the "Chinese Virus" by a president of the country has contributed to an environment of racial discrimination and hatred against Asians.
+Therefore, they became dissatisfied with Trump and more supportive to Biden, whose policies are more open and democratic, and values racial equality more.
 
 Most white people vote relatively evenly, due to the fact that they are not affected by immigration or other policies.
-Whites hold a major voice and position in the US, most of the ideas and policies Trump proposes are favorable to whites.
-Therefore, he can gain support from most whites.
-However, there are some whites who want a democratic and equal environment, and at the same time do not want to see racial discrimination and other phenomena, so they will choose to support Biden, who values equality.
+Whites hold a major voice and position in the US; most of the ideas and policies Trump proposes are favorable to whites.
+Therefore, he gains some support from White people.
+However, there are people who want a democratic and equal environment, and at the same time do not want to see racial discrimination and other phenomena, so they will choose to support Biden, who values equality.
 
@@
 
-Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes.
+Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes [@wiki2020].
 This support is particularly evident in cities within these regions, driven by various factors including liberal ideals and progressive policies.
@@
 
-modelplot(political_preferences1, conf_level = 0.90, size = 0.1) +
+modelplot(political_preferences1, conf_level = 0.90, size = 0.2) +
   labs(x = "90% credibility interval")
@@
 # Create the model plot
-model_plot <- modelplot(political_preferences1, conf_level = 0.9)
+model_plot <- modelplot(political_preferences1, conf_level = 0.9, , size = 0.2)
 

### 2024-03-16 paper/us_election_2020.qmd
render paper

@@
 
+Our discussion is made based on @tbl-modelresults1 from our model, as well as background information on different presidential candidates and their different views of the world and divergent approaches to tackling some of the  issues in the United States.
+
 ## Racial Variations
+In the United States, race is always a sensitive topic.
+Many racist and discriminating events have happened in the past in this country that people in minority groups have to endure.
+As Trump and Biden have different ideology in guaranteeing racial equality [@biden_inclusion], it is obvious that being in different racial groups will influence people's decision in voting.
 
@@
 Southern states, such as Alabama, Mississippi, and South Carolina with a large amount of Christian population, strongly adhere to conservative principles.
-For example, these states have implemented strict anti-abortion law and advocated for tight immigration policies.
+For example, these states have implemented strict anti-abortion law [@abortion] and advocated for tight immigration policies.
 Furthermore, these states have historically been less supportive of LGBTQ+ rights.
@@
 
-Individuals employed part-time, laid-off, or unemployed demonstrate a notable support towards Biden, a trend likely attributed to Biden's alignment with policies favoring these groups, such as enhanced benefits and support programs [@williams_2020].
+Individuals employed full-time, part-time, laid-off, or unemployed demonstrate a notable support towards Biden, a trend likely attributed to Biden's alignment with policies favoring these groups, such as enhanced benefits and support programs [@williams_2020].
 For example, Biden and his party advocate for extending unemployment benefits, providing relief for laid-off workers, and bolstering job creation initiatives to address economic challenges faced by these individuals.

### 2024-03-16 paper/us_election_2020.qmd
some edit

@@
 
-3. region: the census region where the respondent lives; numeric numbers starting from 1 correspond to options "Northeast", "Midwest", "South", and "West", respectively.
+3.
+race: the racial or ethnic group of the respondent; numeric numbers starting from 1 correspond to options "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other", respectively.
 
-4.
-race: the racial or ethnic group of the respondent; numeric numbers starting from 1 correspond to options "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other", respectively.
+4. region: the census region where the respondent lives; numeric numbers starting from 1 correspond to options "Northeast", "Midwest", "South", and "West", respectively.
 
@@
 To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.
-Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see -@sec-model-details).
+Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix @sec-model-details).
 
@@
 
-More detailed explanation of each plot can be found in -@sec-model-details.
+More detailed explanation of each plot can be found in Appendix @sec-model-details.
 
@@
 
-Our discussion is made based on @tbl-modelresults1 from our model, as well as background information on different presidential candidates and their different views of the world and divergent approaches to tackling some of the  issues in the United States.
+Our discussion is made primarily based on the logistic regression model and its result in @tbl-modelresults1, as well as background information on different presidential candidates and their different views of the world and divergent approaches to tackling some of the  issues in the United States.
 

### 2024-03-16 paper/us_election_2020.qmd
render paper

@@
 
-# Additional data details
+## Model details {#sec-model-details}
 
-# Model details {#sec-model-details}
-
-## Posterior predictive check
+### Posterior predictive check
 In @fig-post_dist, we implement a posterior distribution.
@@
 
-posterior_vs_prior(political_preferences1) +
+posterior_vs_prior(political_preferences1, size = 0.3) +
   theme_minimal() +
@@
 
-## Credibility Interval {#sec-credibility-interval}
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-modelresults1
-#| fig-cap: "Credible intervals for predictors of support for Biden 1"
-
-modelplot(political_preferences1, conf_level = 0.90, size = 0.2) +
-  labs(x = "90% credibility interval")
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-modelresults2
-#| fig-cap: "Credible intervals for predictors of support for Biden 2"
-# Create the model plot
-model_plot <- modelplot(political_preferences1, conf_level = 0.9, , size = 0.2)
-
-# Modify the x-axis limits
-model_plot + xlim(-5, 5) +  # Adjust the limits as needed
-  labs(x = "90% Credibility Interval")
-```
-
-## Markov chain Monte Carlo Convergence Check
+### Markov chain Monte Carlo Convergence Check
 
@@
 
+### Credibility Interval {#sec-credibility-interval}
+90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of support for Biden 1"
+
+modelplot(political_preferences1, conf_level = 0.90, size = 0.2) +
+  labs(x = "90% credibility interval")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults2
+#| fig-cap: "Credible intervals for predictors of support for Biden 2"
+# Create the model plot
+model_plot <- modelplot(political_preferences1, conf_level = 0.9, , size = 0.2)
+
+# Modify the x-axis limits
+model_plot + xlim(-5, 5) +  # Adjust the limits as needed
+  labs(x = "90% Credibility Interval")
+```
+
 \newpage

### 2024-03-16 paper/us_election_2020.qmd
final edits

--- 2024-03-16 paper/us_election_2020.qmd
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
@@
   coord_flip()
-```
-
-## Credibility Interval {#sec-credibility-interval}
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-modelresults1
-#| fig-cap: "Credible intervals for predictors of support for Biden 1"
-
-modelplot(political_preferences1, conf_level = 0.90, size = 0.2) +
-  labs(x = "90% credibility interval")
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-modelresults2
-#| fig-cap: "Credible intervals for predictors of support for Biden 2"
-# Create the model plot
-model_plot <- modelplot(political_preferences1, conf_level = 0.9, , size = 0.2)
-
-# Modify the x-axis limits
-model_plot + xlim(-5, 5) +  # Adjust the limits as needed
-  labs(x = "90% Credibility Interval")
 ```
@@
 
+## Credibility Interval {#sec-credibility-interval}
+90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of support for Biden 1"
+
+modelplot(political_preferences1, conf_level = 0.90, size = 0.2) +
+  labs(x = "90% credibility interval")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults2
+#| fig-cap: "Credible intervals for predictors of support for Biden 2"
+# Create the model plot
+model_plot <- modelplot(political_preferences1, conf_level = 0.9, , size = 0.2)
+
+# Modify the x-axis limits
+model_plot + xlim(-5, 5) +  # Adjust the limits as needed
+  labs(x = "90% Credibility Interval")
+```
+
 \newpage

### 2024-03-16 paper/us_election_2020.qmd
edit based on peer review

@@
 
-```{r}
-#| include: false
-# Extract posterior samples
-# posterior_samples <- as.matrix(political_preferences)
-# 
-# # Calculate credible intervals (e.g., 95%)
-# credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))
-# 
-# # Extract coefficient names
-# coefficient_names <- colnames(posterior_samples)
-# 
-# # Create a data frame with coefficient names, coefficient estimates, and credible intervals
-# table_data <- data.frame(
-#   Posterior_Mean = colMeans(posterior_samples),
-#   Credible_Interval_Lower = credible_intervals[1, ],
-#   Credible_Interval_Upper = credible_intervals[2, ]
-# )
-# 
-# # Print the table
-# print(table_data)
-
-```
-
 @fig-modelresults1 (see @sec-credibility-interval) shows range of coefficient estimates of our model within the 90% probability.
@@
 90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
+@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability.
+Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
+Therefore we created figure @fig-modelresults2 with the x axis limited from -10 to 10.
+
+Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
+The estimates are significant if the intervals do not cross 0.
+The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
 

### 2024-03-16 paper/us_election_2020.qmd
update appendix

@@
 
-## Data Result
+## Data Results
 
@@
 Our results generally matches our expectation.
-To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.
+The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
 In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.
@@
   theme(legend.position = "bottom") +
+  theme(axis.text.x=element_text(hjust=1, vjust=0.5),
+        text=element_text(size=8)) +
   coord_flip()
@@
 
-@fig-trace is a trace plot.
+@fig-trace1, @fig-trace2, @fig-trace3 are the trace plot of the model.
 It shows if there is existence of signs that the our model runs into issues.
@@
 
-@fig-rhat is a Rhat plot.
+@fig-rhat is the Rhat plot of the model.
 It compares the variability within each chain to the variability between chains in MCMC.
@@
 #| warning: false
-#| label: fig-trace
-#| fig-cap: "Trace plot"
+#| label: fig-trace1
+#| fig-cap: "Trace plot of intercept and race"
+#| fig-subcap: ["Trace plot of Intercept", "Trace plot of race White", "Trace plot of race Black", "Trace plot of race Hispanic", "Trace plot of race Middle Eastern", "Trace plot of race Native American", "Trace plot of race Two or more races", "Trace plot of race Other"]
+#| layout-ncol: 2
 
- plot(political_preferences1, "trace")
+#plot(political_preferences1, "trace")
+plot(political_preferences1, "trace", "(Intercept)")
+
+plot(political_preferences1, "trace", "raceWhite")
+plot(political_preferences1, "trace", "raceBlack")
+plot(political_preferences1, "trace", "raceHispanic")
+plot(political_preferences1, "trace", "raceMiddle Eastern")
+plot(political_preferences1, "trace", "raceNative American")
+plot(political_preferences1, "trace", "raceTwo or more races")
+plot(political_preferences1, "trace", "raceOther")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-trace2
+#| fig-cap: "Trace plot of region"
+#| fig-subcap: ["Trace plot of region Northeast", "Trace plot of region South", "Trace plot of region West"]
+#| layout-ncol: 2
+
+plot(political_preferences1, "trace", "regionNortheast")
+plot(political_preferences1, "trace", "regionSouth")
+plot(political_preferences1, "trace", "regionWest")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-trace3
+#| fig-cap: "Trace plot of employ"
+#| fig-subcap: ["Trace plot of employ Homemaker", "Trace plot of employ Part-time", "Trace plot of employ Permanently disabled", "Trace plot of employ Retired", "Trace plot of employ Student", "Trace plot of employ Temporarily laid off", "Trace plot of employ Unemployed", "Trace plot of employ Other"]
+#| layout-ncol: 2
+
+plot(political_preferences1, "trace", "employHomemaker")
+plot(political_preferences1, "trace", "employPart-time")
+plot(political_preferences1, "trace", "employPermanently disabled")
+plot(political_preferences1, "trace", "employRetired")
+plot(political_preferences1, "trace", "employStudent")
+plot(political_preferences1, "trace", "employTemporarily laid off")
+plot(political_preferences1, "trace", "employUnemployed")
+plot(political_preferences1, "trace", "employOther")
 ```
@@
 90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
-@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability.
-Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables.
-Therefore we created figure @fig-modelresults2 with the x axis limited from -10 to 10.
-
-Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time.
-The estimates are significant if the intervals do not cross 0.
-The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
 

### 2024-03-16 scripts/04-model.R
fix model tests

@@ -11,7 +11,7 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
-
+library(testthat)
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/cleaned_ces2020.csv")
 
@@ -46,7 +46,7 @@ saveRDS(
   file = "models/political_preferences1.rds"
 )
 
-test_file("scripts/test_class.R")
-test_file("scripts/test_observations.R")
-test_file("scripts/test_coefficients.R")
+test_file("scripts/05-test_class.R")
+test_file("scripts/06-test_observations.R")
+test_file("scripts/07-test_coefficients.R")
 

### 2024-03-16 paper/us_election_2020.qmd
changes
resolve reference issues and minor changes

--- 2024-03-16 paper/us_election_2020.qmd
@@
 
-Our dataset's quantitative representation of real-world phenomena is influenced by several factors, which inherently limit the accuracy of our measurements for the five variables.
+Because our dataset is survey-based, the measurement accuracy of our five variables might be influenced by many external factors.
 
@@
 Additionally, students working part-time jobs may selectively report their status based on their perceived benefit.
-These discrepancies can introduce bias and inaccuracies into the data, impacting the reliability of our analyses.
+These inconsistencies can introduce bias and inaccuracies into the data, impacting the reliability of our analyses.
 
@@
 These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump.
-States such as Texas and Florida, which are known Republican strongholds, are located in the South.
+States, such as Texas, which are known Republican strongholds, are located in the South.
 Therefore, individuals in these regions may be less inclined to support Biden's progressive agenda.
@@
 
-The trace plot in @fig-trace does not suggest anything out of the ordinary.
+The trace plots in @fig-trace1, @fig-trace2, and @fig-trace3 do not suggest anything out of the ordinary.
 Also, with the Rhat plot (@fig-rhat), we can observe that everything is close to 1, and no more than 1.05, which shows the great convergence of Markov chain Monte Carlo for our model.
@@
 ## Credibility Interval {#sec-credibility-interval}
-90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
 

### 2024-03-16 paper/us_election_2020.qmd
final edits

@@
 We expect a positive relationship between individuals of Black, Asian, and Hispanic ethnicities and their support for Biden.
-This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall [@trump_wall].
+This expectation arises from Trump's history of spreading polarizing language and anti-immigrant sentiments, as well as his controversial plans such as building a border wall [@Rodriguez_2021].
 These groups are more likely to align with Biden's policies, which prioritize inclusion and diversity [@biden_inclusion].
@@
 Conversely, we anticipate a negative relationship between voters in the South and Midwest regions and support for Biden.
-These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump.
+These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump [@wiki_south].
 States, such as Texas, which are known Republican strongholds, are located in the South.
@@
 Students are often exposed to diverse perspectives and progressive ideas in educational settings, making them more likely to endorse Biden's platform.
-Unemployed and laid-off individuals may favor Biden due to the Democratic Party's advocacy for social welfare programs and support for workers' rights.
+Unemployed and laid-off individuals may favor Biden due to the Democratic Party's advocacy for social welfare programs and support for workers' rights [@wiki_biden].
 
@@
 Trump claimed the wall reformed the immigration system and achieved the most secure southern border in US history.
-However, that was not true, and with it had come a surge in illegal border crossings [@trump_wall], which overall made Hispanic people dissatisfied with Trump's decisions and ruling.
+However, that was not true, and with it had come a surge in illegal border crossings [@Rodriguez_2021], which overall made Hispanic people dissatisfied with Trump's decisions and ruling.
 
 As COVID-19 pandemics spreaded, Trump repeatedly called it "Chinese virus" [@trump_virus].
-This obviously led to a large number of Asians, especially Chinese people, feel targeted becuase it is an extremely anti-Asian statement: although COVID-19 was first found in China, but it does not mean that virus was from China.
-Trump's comments quickly festered in public opinion and led to a dramatic increase in hate incidents in the Asian American community [@Reja_2021].
-The repeated use of the "Chinese Virus" by a president of the country has contributed to an environment of racial discrimination and hatred against Asians.
-Therefore, they became dissatisfied with Trump and more supportive to Biden, whose policies are more open and democratic, and values racial equality more.
+This obviously led to a large number of Asians, especially Chinese people, feel targeted because it is an extremely anti-Asian statement: although COVID-19 was first found in China, but it does not mean that virus was from China.
+The repeated use of the "Chinese Virus" by a president of the country quickly festered in public opinion and led to a dramatic increase in racial discrimination and hate incidents towards Asian American communities [@Reja_2021].
+Therefore, they became dissatisfied with Trump and more supportive to Biden, whose policies are more open and democratic, and values racial equality more [@wiki_biden].
 
@@
 Our analysis highlights regional voting variations, with the Northeast, West, and Midwest favoring Biden, while the South supports Trump.
-These differences stem from diverse cultural, family, religious, and social perspectives.
+These differences stem from diverse cultural, religious, and social perspectives based on regions.
 
@@
 For instance, states like New York and Massachusetts support Biden due to their liberal-leaning populations, diverse demographics, and emphasis on social justices.
-Similarly, on the West Coast, states such as California and Washington are known for their progressive values and advocacy for issues like environmental conservation and LGBTQ+ rights, contributing to Biden's popularity in these areas.
+Similarly, on the West Coast, states such as California and Washington are known for their progressive values and advocacy for issues like environmental conservation and LGBTQ+ rights[@lgbtq], contributing to Biden's popularity in these areas.
 In the Southwest, states like Arizona and Nevada, with growing minority populations and concerns over immigration policies, also show significant support for Biden.
@@
 Additionally, Biden's support for racial equality and social justice initiatives aligns with the progressive values often embraced by college students.
+
+It is evident that Trump gained more support from homemakers, retirees, and permanently disabled individuals.
+This preference could be due to the fact that these groups may not be directly impacted by the economic policies proposed by either candidate.
+Thus, their voting decisions may be influenced by other campaign aspects.
+Biden's focus on creating job opportunities and raising minimum wages may strongly resonate with those who are actively working or seeking employment [@biden_inclusion], but it may not hold as much relevance for homemakers, retirees, and the permanently disabled.
 

### 2024-03-16 paper/us_election_2020.qmd
final changes

@@
 ---
-title: "Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election"
+title: "Understanding the Impact of Race, Region, and Employment on Voter Behavior: An Analysis of the 2020 U.S. Presidential Election"
 author: 
@@
 For instance, states like New York and Massachusetts support Biden due to their liberal-leaning populations, diverse demographics, and emphasis on social justices.
-Similarly, on the West Coast, states such as California and Washington are known for their progressive values and advocacy for issues like environmental conservation and LGBTQ+ rights[@lgbtq], contributing to Biden's popularity in these areas.
+Similarly, on the West Coast, states such as California and Washington are known for their progressive values and advocacy for issues like environmental conservation and LGBTQ+ rights, contributing to Biden's popularity in these areas.
 In the Southwest, states like Arizona and Nevada, with growing minority populations and concerns over immigration policies, also show significant support for Biden.

### 2024-03-16 paper/us_election_2020.qmd
final edits
some edits

@@
 Four years ago, the United States was at the forefront of an important electoral contest between the Democratic and Republican parties in the 2020 presidential election.
-The Democratic and Republican parties are represented by Donald Trump and Joe Biden respectively [@wiki2020].
-Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton [@result2016].
+The Democratic and Republican parties are represented by Donald Trump and Joe Biden respectively.
+Donald Trump achieved a remarkable victory in the 2016 election against Hillary Clinton.
 On the other hand, Joe Biden led the Democratic campaign.
@@
 
-Our discussion is made primarily based on the logistic regression model and its result in @tbl-modelresults1, as well as background information on different presidential candidates and their different views of the world and divergent approaches to tackling some of the  issues in the United States.
+Our discussion is made primarily based on the logistic regression model and its result in @tbl-modelresults1, as well as background information on the two presidential candidates, Trump and Biden, and their different views of the world and divergent approaches to tackling some of the issues in the United States.
 
@@
 ## Credibility Interval {#sec-credibility-interval}
+@fig-modelresults1 and @fig-modelresults2 show the 90% credibility interval for the model.
 
@@
 #| label: fig-modelresults1
-#| fig-cap: "Credible intervals for predictors of support for Biden 1"
+#| fig-cap: "Credible intervals for predictors of support for Biden"
 
@@
 #| label: fig-modelresults2
-#| fig-cap: "Credible intervals for predictors of support for Biden 2"
+#| fig-cap: "Credible intervals for predictors of support for Biden with x_axis limits"
 # Create the model plot

### 2024-03-16 paper/us_election_2020.qmd
some edits

@@
 
-Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes [@wiki2020].
+Biden's support base is concentrated in the Mid-Atlantic states, New England, the West Coast, Southwestern states, and certain regions around the Great Lakes.
 This support is particularly evident in cities within these regions, driven by various factors including liberal ideals and progressive policies.
